---
title: "Attrition in Dog Survey"
author: "Riqi Xu"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(svglite)
library(tidyverse)
library(stringr)
library(dplyr)
library(ggplot2)
library(scales)
library(survival)
library(patchwork)
library(flextable)
library(officer)
library(forcats)
library(broom)
library(ggrepel)
```

# Step 1: Preliminary Exploration of National Dog Survey 2023 Structure
```{r}
# Import Dataset with Strict Type Guessing Fix
# Setting guess_max = Inf ensures text codes like 'NAQ' are not corrupted into logical NA
data_path <- "NDS_2023_attrition_data.csv"
raw_data <- read_csv(data_path, guess_max = Inf, show_col_types = FALSE)

# Verify Full Dataset Dimensions
data_structure <- tibble(records = nrow(raw_data), variables = ncol(raw_data),
  character_columns = sum(map_lgl(raw_data, is.character)),
  numeric_columns = sum(map_lgl(raw_data, is.numeric)),
  logical_columns = sum(map_lgl(raw_data, is.logical)))
print(data_structure)

# Check Baseline Target Variable: Survey Completion Status
completion_summary <- raw_data %>%
  count(Finished, name = "responses") %>%
  mutate(status = case_when(is.na(Finished) ~ "Missing",
      Finished ~ "Completed", TRUE ~ "Not completed"),
    percentage = round(responses / sum(responses) * 100, 2)) %>%
  select(status, responses, percentage)
print(completion_summary)
```

# Step 2: Locating the Precise Drop-out Points and Computing Hazards
# Node-Level Timeline Tracking & Terminal Extraction
```{r}
# Step 2: Node-Level Timeline Tracking & Terminal Extraction
# NAQ-aware version to capture visual exposure dropout

# 2.1 Define raw question columns
raw_question_columns <- names(raw_data)[10:247]

# 2.2 Establish Raw-Field-to-Page-Node Mapping
# Explicit mapping for fields displayed on the same page
page_merge_map <- tribble(
  ~raw_col,                         ~page_node_id,
  
  # Main owner route
  "Q4_DogAge.1_1",                  "Q4_DogAge",
  "Q4_DogAge.2_1",                  "Q4_DogAge",
  "Q6.2_DogBreed_1",                "Q6.2_DogBreed",
  "Q6.2_DogBreed_2",                "Q6.2_DogBreed",
  "Q7_DogCrop",                     "Q7_DogCropDock",
  "Q7_DogDock",                     "Q7_DogCropDock",
  "Q14_Worries_Living",             "Q14_Worries",
  "Q14_Worries_Employment",         "Q14_Worries",
  "Q14_Worries_DailyRoutine",       "Q14_Worries",
  "Q14_Worries_Family",             "Q14_Worries",
  "Q14_Worries_CoL",                "Q14_Worries",
  "Q15_CostPressure_1",             "Q15_CostPressure",
  "Q15_CostPressure_2",             "Q15_CostPressure",
  "Q15_CostPressure_3",             "Q15_CostPressure",
  "Q15_CostPressure_4",             "Q15_CostPressure",
  
  # Second-dog route
  "Q204_DogAge.1_1",                "Q204_DogAge",
  "Q204_DogAge.2_1",                "Q204_DogAge",
  "Q208_DogBreed_1",                "Q208_DogBreed",
  "Q208_DogBreed_2",                "Q208_DogBreed",
  "Q211_DogCrop",                   "Q211_DogCropDock",
  "Q211_DogDock",                   "Q211_DogCropDock",
  
  # Third-dog route
  "Q304_DogAge.1_1",                "Q304_DogAge",
  "Q304_DogAge.2_1",                "Q304_DogAge",
  "Q308_DogBreed_1",                "Q308_DogBreed",
  "Q308_DogBreed_2",                "Q308_DogBreed",
  "Q311_DogCrop",                   "Q311_DogCropDock",
  "Q311_DogDock",                   "Q311_DogCropDock",
  
  # Fourth-dog route
  "Q404_DogAge.1_1",                "Q404_DogAge",
  "Q404_DogAge.2_1",                "Q404_DogAge",
  "Q408_DogBreed_1",                "Q408_DogBreed",
  "Q408_DogBreed_2",                "Q408_DogBreed",
  "Q411_DogCrop",                   "Q411_DogCropDock",
  "Q411_DogDoc",                    "Q411_DogCropDock",
  
  # Fifth-dog route
  "Q504_DogAge.1_1",                "Q504_DogAge",
  "Q504_DogAge.2_1",                "Q504_DogAge",
  "Q508_DogBreed_1",                "Q508_DogBreed",
  "Q508_DogBreed_2",                "Q508_DogBreed",
  "Q511_DogCrop",                   "Q511_DogCropDock",
  "Q511_DogDock",                   "Q511_DogCropDock",
  
  # E11 ethnicity selection and its optional text field
  "E11.1_EthnicityText",            "E11_Ethnicity"
)

# Build final question_map combining regex logic and explicit mapping
question_map <- tibble(
  raw_col = raw_question_columns,
  raw_order = seq_along(raw_question_columns)
) %>%
  mutate(base_node_id = raw_col %>%
           str_replace("(_\\d+)?_TEXT$", "") %>%
           str_replace("_text$", "")) %>%
  left_join(page_merge_map, by = "raw_col") %>%
  mutate(node_id = coalesce(page_node_id, base_node_id)) %>%
  select(raw_col, raw_order, node_id)

# Preserve chronological page order
node_order <- question_map %>%
  group_by(node_id) %>%
  summarise(node_order = min(raw_order), .groups = "drop") %>%
  arrange(node_order)

node_ids <- node_order$node_id

# 2.3 Define NAQ-aware recorded responses
# This treats NAQ as a system-recorded visual exposure value, excluding true skip-logic blanks (NA) and empty strings
is_recorded_response <- function(x) {
  if (is.character(x) || is.factor(x)) {
    y <- str_trim(as.character(x))
    return(!is.na(y) & y != "")
  } else {
    return(!is.na(x))
  }
}

# Valid substantive response:
# excludes missing values, empty strings and the literal NAQ placeholder
is_valid_response <- function(x) {
  if (is.character(x) || is.factor(x)) {
    y <- str_trim(as.character(x))

    !is.na(y) &
      y != "" &
      str_to_upper(y) != "NAQ"
  } else {
    !is.na(x)
  }
}

# Generate recorded-response matrix for raw columns
raw_recorded_df <- raw_data %>%
  select(all_of(raw_question_columns)) %>%
  mutate(across(everything(), is_recorded_response))

# 2.4 Aggregate into node-level recorded matrix (Logic OR Gate)
# A node is TRUE if the parent or any merged child field has any recorded value, including NAQ
recorded_node_matrix <- sapply(node_ids, function(nd) {
  cols_for_node <- question_map$raw_col[question_map$node_id == nd]
  
  rowSums(
    as.data.frame(raw_recorded_df[, cols_for_node, drop = FALSE]),
    na.rm = TRUE
  ) > 0
})

recorded_node_matrix <- as.matrix(recorded_node_matrix)
storage.mode(recorded_node_matrix) <- "logical"

# NAQ-aware recorded node count
raw_data$nodes_seen <- rowSums(recorded_node_matrix, na.rm = TRUE)

# 2.5 Extract terminal event node (Last recorded node, including NAQ)
last_recorded_index <- apply(recorded_node_matrix, 1, function(row) {
  idx <- which(row == TRUE)
  
  if (length(idx) == 0) {
    return(NA_integer_)
  }
  
  return(max(idx))
})

raw_data$terminal_node <- "Pre_Survey_Bounce"

valid_recorded_terminal <- !is.na(last_recorded_index)

raw_data$terminal_node[valid_recorded_terminal] <-
  node_ids[last_recorded_index[valid_recorded_terminal]]

# 2.6 Print final terminal dropout hotspots for validation
terminal_hotspots_node <- raw_data %>%
  filter(Finished == FALSE) %>%
  count(terminal_node, sort = TRUE) %>%
  mutate(percent = n / sum(n) * 100)

print(head(terminal_hotspots_node, 15))


raw_seen_df <- raw_data %>%
  select(all_of(raw_question_columns)) %>% # 去掉了 dplyr:: 前缀
  mutate(across(everything(), is_valid_response))

seen_node_matrix <- sapply(node_ids, function(nd) {
  cols_for_node <- question_map$raw_col[question_map$node_id == nd]
  
  rowSums(
    as.data.frame(raw_seen_df[, cols_for_node, drop = FALSE]),
    na.rm = TRUE
  ) > 0
})

seen_node_matrix <- as.matrix(seen_node_matrix)
storage.mode(seen_node_matrix) <- "logical"
raw_data$nodes_seen <- rowSums(seen_node_matrix, na.rm = TRUE)
```

```{r}
owner_answers <- c("One", "Two", "Three", "Four", "Five or more (please specify)")

route_audit_data <- raw_data %>%
  mutate(consent_clean = str_squish(
      as.character(ConsentToSurvey) ),
    consent_clean = na_if(consent_clean, ""),

    q1_clean = str_squish( as.character(Q1_DogNumber) ),
    q1_clean = na_if(q1_clean, ""),

    finished_flag = str_to_upper(as.character(Finished)) == "TRUE",
    questionnaire_entry = !is.na(consent_clean),
    route_group = case_when( !questionnaire_entry ~ "Pre-questionnaire exit",

      q1_clean %in% owner_answers ~ "Dog-owner",
      q1_clean == "I don't have a dog" ~ "Non-owner",
      TRUE ~  "Pre-route/undetermined"),

    terminal_status = case_when(
      route_group == "Pre-questionnaire exit" ~ "Pre-questionnaire exit",
      consent_clean == "No" & finished_flag ~  "Consent declined (routed end)",
      finished_flag ~  "Completed questionnaire",
      TRUE ~ "Question-level breakoff" )
  )
```

```{r}
route_summary <- route_audit_data %>%
  filter(questionnaire_entry) %>%
  group_by(route_group) %>%
  summarise(
    entrants = n(),

    completed_questionnaires =
      sum(terminal_status == "Completed questionnaire"),

    consent_declined =
      sum(terminal_status == "Consent declined (routed end)"),

    breakoffs =
      sum(terminal_status == "Question-level breakoff"),

    breakoff_rate = 100 * breakoffs / entrants,

    .groups = "drop" ) %>%
  mutate(
    entrant_share = 100 * entrants / sum(entrants)
  ) %>%
  select( route_group, entrants, entrant_share, completed_questionnaires,
    consent_declined, breakoffs, breakoff_rate)

print(route_summary)
```


# Step 3: Empirical Baseline Lifetable & Survival Curve
## Generate Node Metadata Dictionary for Feature Engineering
```{r metadata-draft, eval=FALSE}
# Step 3A & 3B: Generate Node Metadata Dictionary for Feature Engineering
# Constructs a metadata dictionary to map structural and psychological traits to each survey node

# Identify parent nodes that contain derivative child text-entry fields
text_child_nodes <- question_map %>%
  filter(str_detect(raw_col, "_TEXT$|_text$")) %>%
  distinct(node_id) %>%
  pull(node_id)

# Build the foundational metadata dictionary
node_metadata <- tibble(
  node_id = node_ids
) %>%
  mutate(
    # Route and branching logic indicators
    route = case_when(
      str_starts(node_id, "E") ~ "non_owner_exit",
      str_detect(node_id, "^Q2(0[1-9]|1[0-9]|20)") ~ "second_dog",
      str_detect(node_id, "^Q3(0[1-9]|1[0-9]|20)") ~ "third_dog",
      str_detect(node_id, "^Q4(0[1-9]|1[0-9]|20)") ~ "fourth_dog",
      str_detect(node_id, "^Q5(0[1-9]|1[0-9]|20)") ~ "fifth_dog",
      TRUE ~ "owner_main"
    ),
    
    route_simplified = case_when(
      str_detect(route, "second_dog|third_dog|fourth_dog|fifth_dog") ~ "repeated_dogs_loop",
      route == "non_owner_exit" ~ "non_owner_exit",
      TRUE ~ "owner_main"
    ),
    
    # Dimension 1: Cognitive Burden and UI Design Attributes
    
    # Identify true matrix/grid format questions
    is_matrix = as.integer(
      str_detect(node_id, "Matrix|Worries|Scale|Rating")
    ),
    
    # Flag presence of child text entry boxes (e.g., 'Other, please specify')
    has_child_text_entry = as.integer(
      node_id %in% text_child_nodes
    ),
    
    # Flag primary open-ended text questions
    is_main_open_text = as.integer(
      str_detect(node_id, "DogName|ImproveLife|WelfareIssues|Comment|Specify")
    ),
    
    # Flag short text or personal input fields
    is_short_text = as.integer(
      str_detect(node_id, "Postcode|Phone|Email")
    ),
    
    # Aggregate flag for any form of text entry requirement
    has_text_entry = as.integer(
      has_child_text_entry == 1 |
        is_main_open_text == 1 |
        is_short_text == 1
    ),
    
    text_entry_type = case_when(
      is_main_open_text == 1 ~ "main_open_text",
      is_short_text == 1 ~ "short_text_identifier",
      has_child_text_entry == 1 ~ "optional_child_text",
      TRUE ~ "none"
    ),
    
    # Placeholders for manual annotation based on the survey PDF
    word_count = NA_integer_,
    options_count = NA_integer_,
    
    # Flag questions with extensive response options
    is_long_choice = as.integer(
      str_detect(node_id, "ServicesCutCoL|HolidayAccommo|DogDaytime|DogSource|DogAversive")
    ),
    
    # Dimension 2: Psychological Sensitivity and Topic Categorization
    
    privacy_level = case_when(
      str_detect(node_id, "Postcode|Phone|Email|DogName") ~ "High",
      str_detect(node_id, "Ethnicity|Gender|Age|Housing|Household|Education|Income") ~ "Medium",
      TRUE ~ "Low"
    ),
    
    financial_sensitivity = as.integer(
      str_detect(node_id, "Cost|CoL|Vet|Insurance|Expense|Spend|Service|Money|Affordable")
    ),
    
    topic_category = case_when(
      str_detect(node_id, "DogName|DogNumber|DogAge|DogSex|DogBreed") ~ "Dog_Profile",
      str_detect(node_id, "DogSource|DogRegionBorn|DogEuropeBorn|DogWorldBorn") ~ "Dog_Acquisition",
      str_detect(node_id, "DogDaytime|DogWorkBarrier") ~ "Dog_Care_Routine",
      str_detect(node_id, "DogReward|DogAversive|AversTool|Behaviour") ~ "Dog_Behavior",
      str_detect(node_id, "Holiday") ~ "Dog_Holiday_Care",
      str_detect(node_id, "Cost|CoL|Services|Vet|Insurance|Expense|Spend") ~ "Financial_Cost",
      str_detect(node_id, "Welfare|DTInternational|DTFoster|GovRole|ImproveLife") ~ "Dog_Welfare",
      str_detect(node_id, "Age|Gender|Ethnicity|Housing|Postcode|Household|Income") ~ "Owner_Demographics",
      str_starts(node_id, "E") ~ "Non_Owner_Exit",
      TRUE ~ "Other"
    ),
    
    # Dimension 3: Recall Effort
    
    requires_precise_recall = as.integer(
      str_detect(node_id, "When|Year|Month|Date|HowOften|Frequency|Spend|Cost|Amount|Age")
    ),
    
    # Derived heuristic scores for robustness checks
    
    cognitive_burden_score = case_when(
      is_matrix == 1 ~ 3L,
      is_long_choice == 1 ~ 3L,
      is_main_open_text == 1 ~ 3L,
      has_text_entry == 1 ~ 2L,
      requires_precise_recall == 1 ~ 2L,
      TRUE ~ 1L
    ),
    
    sensitivity_score = case_when(
      privacy_level == "High" ~ 3L,
      privacy_level == "Medium" ~ 2L,
      financial_sensitivity == 1 ~ 2L,
      TRUE ~ 1L
    ),
    
    # Flag for nodes requiring strict manual verification
    manual_check_needed = as.integer(
      is_matrix == 1 |
        has_text_entry == 1 |
        is_long_choice == 1 |
        privacy_level != "Low" |
        financial_sensitivity == 1 |
        requires_precise_recall == 1
    ),
    
    manual_note = NA_character_
  )

# Export dictionary for subsequent manual refinement
write_csv(node_metadata, "Survey_Node_Metadata_Dictionary_v3.csv")
```


## Appendix A
```{r}
node_metadata <- read_csv("Survey_Node_Metadata_refined.csv", show_col_types = FALSE)
stopifnot(nrow(node_metadata) == 141, !anyDuplicated(node_metadata$node_id))
```

## Appendix_Table_A1_Node_Reconstruction
```{r}
q1_raw_order <- min(question_map$raw_order[question_map$node_id == "Q1_DogNumber"])

table_a1 <- question_map %>%
  group_by(node_id) %>%
  summarise(
    first_raw_order = min(raw_order),
    `Number of source fields` = n_distinct(raw_col),
    `Source raw field(s)` = paste(raw_col, collapse = "; "),
    .groups = "drop"
  ) %>%
  left_join(
    node_metadata %>% select(node_id, route_simplified) %>% distinct(),
    by = "node_id"
  ) %>%
  arrange(first_raw_order) %>%
  mutate(
    `Analytical order` = row_number(),
    `Questionnaire location` = case_when(
      first_raw_order <= q1_raw_order ~ "Pre-route/common",
      route_simplified == "owner_main" ~ "Dog-owner",
      route_simplified == "repeated_dogs_loop" ~ "Repeated-dog module",
      route_simplified == "non_owner_exit" ~ "Non-owner",
      TRUE ~ NA_character_
    )
  ) %>%
  select(
    `Analytical order`,
    `Node ID` = node_id,
    `Questionnaire location`,
    `Number of source fields`,
    `Source raw field(s)`
  )

stopifnot(nrow(table_a1) == 141, !anyNA(table_a1$`Questionnaire location`))

table_a1_ft <- flextable(table_a1) %>%
  set_caption("Table A1. Analytical-node reconstruction dictionary") %>%
  theme_booktabs() %>%
  font(fontname = "Times New Roman", part = "all") %>%
  fontsize(size = 8, part = "all") %>%
  bold(part = "header") %>%
  align(
    j = c("Analytical order", "Number of source fields"),
    align = "center",
    part = "all"
  ) %>%
  valign(valign = "top", part = "all") %>%
  width(j = "Analytical order", width = 0.55) %>%
  width(j = "Node ID", width = 1.30) %>%
  width(j = "Questionnaire location", width = 1.20) %>%
  width(j = "Number of source fields", width = 0.65) %>%
  width(j = "Source raw field(s)", width = 3.40) %>%
  set_table_properties(
  layout = "fixed",
  opts_word = list(
    split = FALSE,
    repeat_headers = TRUE
  )
) %>%
  add_footer_lines(
    "Notes: Raw response fields displayed on the same questionnaire page were combined into one analytical node. Conditional free-text fields were retained within their parent page rather than treated as separate nodes."
  ) %>%
  italic(part = "footer") %>%
  fontsize(size = 7.5, part = "footer")

save_as_docx(
  table_a1_ft,
  path = "Appendix_Table_A1_Node_Reconstruction.docx",
  pr_section = prop_section(
    page_size = page_size(orient = "portrait"),
    page_margins = page_mar(
      top = 0.5, bottom = 0.5, left = 0.5, right = 0.5)
  )
)
```


## Appendix_Table_A2_Metadata_Definitions
```{r}
table_a2 <- tribble(
  ~Variable, ~Definition, ~`Coding/unit`, ~`Analytical use`,
  "route_simplified", "Analytical questionnaire route assigned to the node.", "owner_main; repeated_dogs_loop; non_owner_exit", "Route adjustment and route-specific analyses",
  "has_text_entry", "Whether the node contains required or optional text entry.", "0 = no; 1 = yes", "Main Models 3 and 4",
  "text_entry_type", "Type of text entry presented at the node.", "none; optional_child_text; main_open_text; short_text_identifier", "Metadata audit",
  "options_count", "Number of coded response alternatives associated with the node.", "Count", "Response-format audit",
  "is_long_choice", "Whether the node presents an extended choice set following questionnaire-layout review.", "0 = no; 1 = yes", "Main Models 3 and 4",
  "privacy_level", "Level of personal or identifying information requested.", "Low; Medium; High", "Main Models 3 and 4",
  "financial_sensitivity", "Whether the node concerns expenditure, affordability or financial pressure.", "0 = no; 1 = yes", "Main Models 3 and 4",
  "prompt_word_count", "Number of words in the question or information prompt.", "Words", "Reading-burden measurement",
  "prompt_wc_10", "Prompt length expressed per ten words.", "prompt_word_count / 10", "Main Models 3 and 4",
  "prompt_wc_band_tertile", "Categorical prompt-length measure calculated during analysis.", "Low; Medium; High", "Reading-burden sensitivity analysis",
  "option_word_count_visible", "Number of words in visible response-option labels.", "Words", "Alternative reading-burden specification",
  "total_visible_word_count", "Combined number of prompt and visible option-label words.", "Words", "Alternative reading-burden specification",
  "topic_category", "Substantive topic assigned to the node.", "Categorical", "Topic-category extension",
  "cognitive_burden_score", "Ordinal summary of coded cognitive demands.", "1 = low; 2 = moderate; 3 = high", "Cognitive-burden extension"
)

table_a2_ft <- flextable(table_a2) %>%
  set_caption("Table A2. Definitions and coding of node-level metadata variables") %>%
  theme_booktabs() %>%
  font(fontname = "Times New Roman", part = "all") %>%
  fontsize(size = 8.5, part = "all") %>%
  bold(part = "header") %>%
  valign(valign = "top", part = "all") %>%
  width(j = "Variable", width = 1.4) %>%
  width(j = "Definition", width = 2.7) %>%
  width(j = "Coding/unit", width = 1.2) %>%
  width(j = "Analytical use", width = 1.65) %>%
  set_table_properties(
    layout = "fixed",
    opts_word = list(split = TRUE, repeat_headers = TRUE)
  ) %>%
  add_footer_lines(
    "Notes: Binary indicators use 1 for yes and 0 for no. Shared pre-route/common nodes are coded within owner_main in the analytical metadata. The long-choice indicator was assigned following questionnaire-layout review rather than mechanically from options_count. The legacy word_count_band field was not used in the final categorical sensitivity analysis."
  ) %>%
  italic(part = "footer") %>%
  fontsize(size = 7.5, part = "footer")

save_as_docx(
  table_a2_ft,
  path = "Appendix_Table_A2_Metadata_Definitions.docx",
  pr_section = prop_section(
    page_size = page_size(orient = "portrait"),
    page_margins = page_mar(top = 0.65, bottom = 0.65, left = 0.65, right = 0.65)
  )
)
```




# Step 4: Building Hybrid Person-Period Data
```{r}
# Step 4: Transforming Wide Data to Long Person-Period Survival Matrix
# Integrates the valid-response trajectory with the NAQ-aware terminal event node

# Extract chronological node order
node_order_tbl <- tibble(
  node_id = node_ids,
  node_order = seq_along(node_ids)
)

# 1. Initialize the analysis matrix from the valid-response baseline
analysis_node_matrix <- seen_node_matrix

# Identify unfinished respondents eligible for the node-level attrition model
eligible_event <- (
  raw_data$Finished == FALSE &
  raw_data$nodes_seen > 0 &
  raw_data$terminal_node != "Pre_Survey_Bounce"
)

# Locate the column index of each respondent's terminal event node
terminal_column_index <- match(
  raw_data$terminal_node[eligible_event],
  node_ids
)

if (anyNA(terminal_column_index)) {
  stop("Critical Error: Some terminal_node values are not present in node_ids.")
}

# 2. Inject the terminal NAQ node into the analysis matrix
# This preserves the visually exposed fatal node before wide-to-long transformation
analysis_node_matrix[
  cbind(
    which(eligible_event),
    terminal_column_index
  )
] <- TRUE

nodes_in_analysis <- rowSums(
  analysis_node_matrix,
  na.rm = TRUE
)

# 3. Transform to longitudinal person-period format
person_period_data <- as_tibble(
  analysis_node_matrix,
  .name_repair = "minimal"
) %>%
  mutate(
    ResponseId = raw_data$ResponseId,
    Finished = raw_data$Finished,
    terminal_node = raw_data$terminal_node,
    nodes_in_analysis = nodes_in_analysis
  ) %>%
  filter(nodes_in_analysis > 0) %>%
  pivot_longer(
    cols = all_of(node_ids),
    names_to = "node_id",
    values_to = "in_analysis"
  ) %>%
  filter(in_analysis == TRUE) %>%
  left_join(node_order_tbl, by = "node_id") %>%
  group_by(ResponseId) %>%
  arrange(node_order, .by_group = TRUE) %>%
  mutate(
    time_step = row_number(),
    total_nodes = n(),
    
    # Dynamically assign the hazard event flag (1 = dropout, 0 = censored/survived)
    event = as.integer(
      Finished == FALSE &
      node_id == terminal_node
    )
  ) %>%
  ungroup()
```


## Step 4 Audit: Validating Event Consistency
```{r}
cat("\n--- Step 4 Audit ---\n")
cat("Long data dimensions:", nrow(person_period_data), "rows\n")
cat("Respondents represented:", n_distinct(person_period_data$ResponseId), "\n")

# Calculate expected vs observed events
expected_events <- sum(raw_data$Finished == FALSE & raw_data$terminal_node != "Pre_Survey_Bounce", na.rm = TRUE)
observed_events <- sum(person_period_data$event, na.rm = TRUE)

cat("Expected events:", expected_events, "\n")
cat("Observed events:", observed_events, "\n")

# Verify that no respondent has more than one event
event_count_check <- person_period_data %>%
  group_by(ResponseId) %>%
  summarise(event_count = sum(event), .groups = "drop")

cat("\nEvent-count distribution:\n")
print(table(event_count_check$event_count))
```

## figure3: survival curve
```{r}
# Step 4B: Overall and Route-Conditional Empirical Survival Curves

# 1. Construct one survival record per analytical respondent
respondent_survival <- person_period_data %>%
  group_by(ResponseId) %>%
  summarise(
    time = max(time_step, na.rm = TRUE),
    status = max(event, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  left_join(
    raw_data %>%
      transmute(
        ResponseId,
        q1_clean = str_squish(as.character(Q1_DogNumber)),
        q1_clean = na_if(q1_clean, "")
      ),
    by = "ResponseId"
  ) %>%
  mutate(
    route_group = case_when(
      q1_clean %in% owner_answers ~ "Owner",
      q1_clean == "I don't have a dog" ~ "Non-owner",
      TRUE ~ "Pre-route/undetermined"
    )
  )

# 2. Panel A data: all survey records
# Respondents absent from person_period_data did not reach a
# reconstructable analytical node. Unfinished cases are therefore
# assigned an event at operational time zero.

overall_survival_data <- raw_data %>%
  select(ResponseId, Finished, terminal_node) %>%
  left_join(
    respondent_survival %>%
      select(ResponseId, time, status),
    by = "ResponseId"
  ) %>%
  mutate(
    time = coalesce(time, 0L),
    status = coalesce(
      status,
      as.integer(Finished == FALSE)
    )
  )

# 3. Audit the sample before fitting the curves

panel_a_audit <- overall_survival_data %>%
  summarise(
    total_records = n(),
    pre_survey_bounces = sum(time == 0 & status == 1, na.rm = TRUE),
    survival_after_entry = 1 -
      pre_survey_bounces / total_records
  )

route_audit <- respondent_survival %>%
  group_by(route_group) %>%
  summarise(
    entrants = n(),
    completed_or_censored = sum(status == 0),
    breakoffs = sum(status == 1),
    attrition_rate = breakoffs / entrants,
    .groups = "drop"
  ) %>%
  bind_rows(
    respondent_survival %>%
      summarise(
        route_group = "Overall",
        entrants = n(),
        completed_or_censored = sum(status == 0),
        breakoffs = sum(status == 1),
        attrition_rate = breakoffs / entrants
      )
  )

cat("\n--- Survival Figure Audit ---\n")
print(panel_a_audit)
print(route_audit)

# Expected latest-sample values:
# total_records        = 369,071
# pre_survey_bounces   = 27,274
# survival_after_entry = 92.61%
#
# Overall analytical sample     = 341,797
# Owner entrants                = 321,229
# Non-owner entrants            = 15,737
# Pre-route/undetermined        = 4,831
# Locatable breakoffs           = 95,034

# Stop if the reconstructed samples do not reconcile
stopifnot(
  nrow(overall_survival_data) == nrow(raw_data),
  nrow(respondent_survival) ==
    dplyr::n_distinct(person_period_data$ResponseId),
  sum(respondent_survival$status) ==
    sum(person_period_data$event)
)
```



```{r}
# 4. Function for extracting Kaplan-Meier estimates

extract_km <- function(data, curve_label, add_start = TRUE) {

  fit <- survival::survfit(
    survival::Surv(time, status) ~ 1,
    data = data,
    conf.type = "log-log"
  )

  fit_summary <- summary(fit)

  curve_data <- tibble(
    time = fit_summary$time,
    survival = fit_summary$surv,
    lower = fit_summary$lower,
    upper = fit_summary$upper,
    curve = curve_label
  )

  # Explicitly add S(0) = 1 so that every curve visibly begins at 100%.
  # For Panel A, the next row is also at t = 0 and therefore produces
  # the immediate vertical fall caused by pre-survey bounces.
  if (add_start) {
    curve_data <- bind_rows(
      tibble(
        time = 0,
        survival = 1,
        lower = 1,
        upper = 1,
        curve = curve_label
      ),
      curve_data
    )
  }

  curve_data
}

# 5. Panel A: all records, including the time-zero breakoff

panel_a_data <- extract_km(
  data = overall_survival_data,
  curve_label = "All survey records"
)

n_total <- nrow(overall_survival_data)

n_bounce <- sum(
  overall_survival_data$time == 0 &
    overall_survival_data$status == 1,
  na.rm = TRUE
)

initial_survival <- 1 - n_bounce / n_total

bounce_label <- paste0(
  "Pre-survey bounce: n = ",
  scales::comma(n_bounce),
  " (",
  scales::percent(n_bounce / n_total, accuracy = 0.01),
  ")"
)

panel_a <- ggplot(
  panel_a_data,
  aes(x = time, y = survival)
) +
  geom_ribbon(
    aes(ymin = lower, ymax = upper),
    fill = "#5B6573",
    alpha = 0.14
  ) +
  geom_step(
    color = "#273746",
    linewidth = 1.15,
    direction = "hv"
  ) +
  annotate(
    "label",
    x = 3,
    y = 0.965,
    label = bounce_label,
    size = 3.5,
    hjust = 0,
    linewidth = 0.2,
    fill = "white"
  ) +
  scale_x_continuous(
    breaks = scales::breaks_width(5),
    expand = expansion(mult = c(0.015, 0.02))
  ) +
  scale_y_continuous(
  labels = scales::percent_format(accuracy = 1),
  breaks = seq(0.5, 1, by = 0.05),
  minor_breaks = NULL
  ) +
  coord_cartesian(ylim = c(0.5, 1)) +
  labs(
    title = "Overall survey survival",
    subtitle = paste0(
      "All ",
      scales::comma(n_total),
      " records; survival falls from 100% to ",
      scales::percent(initial_survival, accuracy = 0.01),
      " at questionnaire entry"
    ),
    x = "Cumulative operational nodes encountered",
    y = "Survival probability"
  ) +
  theme_minimal(base_size = 12.5) +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    plot.subtitle = element_text(color = "#5D6D7E", size = 10.5),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank()
  )

# 6. Panel B: route-conditional analytical survival

panel_b_data <- bind_rows(
  extract_km(
    respondent_survival,
    "Overall"
  ),
  extract_km(
    respondent_survival %>%
      filter(route_group == "Owner"),
    "Owner"
  ),
  extract_km(
    respondent_survival %>%
      filter(route_group == "Non-owner"),
    "Non-owner"
  )
) %>%
  mutate(
    curve = factor(
      curve,
      levels = c("Overall", "Owner", "Non-owner")
    )
  )

curve_colours <- c(
  "Overall" = "#273746",
  "Owner" = "#2874A6",
  "Non-owner" = "#D35400"
)

panel_b <- ggplot(
  panel_b_data,
  aes(
    x = time,
    y = survival,
    colour = curve,
    fill = curve,
    group = curve
  )
) +
  geom_ribbon(
    aes(ymin = lower, ymax = upper),
    alpha = 0.07,
    colour = NA
  ) +
  geom_step(
    linewidth = 1.1,
    direction = "hv"
  ) +
  scale_colour_manual(values = curve_colours) +
  scale_fill_manual(values = curve_colours) +
  scale_x_continuous(
    breaks = scales::breaks_width(5),
    expand = expansion(mult = c(0.015, 0.02))
  ) +
  scale_y_continuous(
  labels = scales::percent_format(accuracy = 1),
  breaks = seq(0.5, 1, by = 0.05),
  minor_breaks = NULL
  ) +
  coord_cartesian(ylim = c(0.5, 1)) +
  guides(
    fill = "none",
    colour = guide_legend(
      title = NULL,
      override.aes = list(linewidth = 1.3)
    )
  ) +
  labs(
    title = "Route-conditional survival",
    subtitle = paste0(
      "Conditional on entry into a reconstructable trajectory (n = ",
      scales::comma(nrow(respondent_survival)),
      ")"
    ),
    x = "Cumulative operational nodes encountered",
    y = "Survival probability",
    colour = NULL
  ) +
  theme_minimal(base_size = 12.5) +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    plot.subtitle = element_text(color = "#5D6D7E", size = 10.5),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    legend.position = "top",
    legend.justification = "left"
  )

# 7. Combine Panel A and Panel B
figure3_overall_route_survival <- panel_a / panel_b +
  patchwork::plot_layout(heights = c(1, 1.15)) +
  patchwork::plot_annotation(
    tag_levels = "A",
    theme = theme(
      plot.tag = element_text(face = "bold", size = 13),
      plot.margin = margin(10, 15, 10, 15)
    )
  )

print(figure3_overall_route_survival)

# High-resolution output for the dissertation
ggsave(
  filename = "figure3-overall-route-survival.png",
  plot = figure3_overall_route_survival,
  width = 10,
  height = 10,
  units = "in",
  dpi = 600,
  bg = "white"
)
```



# Step 5
## Step 5A: Empirical Node-Level Hazard and Attrition Volume
```{r}
# Computes absolute dropout volume, empirical hazard rates, and proportional share per node

# 1. Construct the consolidated node-level risk table
node_risk_table <- person_period_data %>%
  group_by(node_id) %>%
  summarise(
    node_order = first(node_order),
    at_risk_n = n(),
    dropouts = sum(event, na.rm = TRUE),
    dropout_rate = dropouts / at_risk_n,
    .groups = "drop"
  ) %>%
  # Calculate the proportional contribution of each node to the total attrition pool
  mutate(
    dropout_share = dropouts / sum(dropouts) * 100
  )

# 2. Identify top nodes by absolute dropout volume
# Highlights questions responsible for the highest raw number of lost respondents
top_by_volume <- node_risk_table %>%
  arrange(desc(dropouts))

# 3. Identify top nodes by empirical hazard (dropout rate)
# Applies a minimum risk set threshold (n >= 500) to prevent small-sample variance on rare branching routes
top_by_rate <- node_risk_table %>%
  filter(at_risk_n >= 500) %>%
  arrange(desc(dropout_rate))

print(top_by_volume, n = 20)
print(top_by_rate, n = 20)
```


## Step 5B: One-vs-Rest Item-Specific Hazard Models
```{r}
# Fits discrete-time logistic models for eligible nodes against the survey baseline,
# controlling for non-linear time, with Benjamini-Hochberg (BH) FDR correction.

# 1. Select the 17 focal nodes for presentation (Union of Top 10 by Count and Rate)
top10_by_count <- node_risk_table %>%
  arrange(desc(dropouts)) %>%
  slice_head(n = 10) %>%
  pull(node_id)

top10_by_rate <- node_risk_table %>%
  filter(at_risk_n >= 500) %>%
  arrange(desc(dropout_rate)) %>%
  slice_head(n = 10) %>%
  pull(node_id)

focal_nodes_to_display <- union(top10_by_count, top10_by_rate)

# 2. Define the global family of eligible nodes for multiple testing correction
# Restricts the testing universe to nodes with sufficient risk set size to prevent sparse data bias
eligible_nodes <- node_risk_table %>%
  filter(at_risk_n >= 500) %>%
  pull(node_id)

# Validate that all selected focal nodes are within the eligible testing family
ineligible_focal_nodes <- setdiff(focal_nodes_to_display, eligible_nodes)
if (length(ineligible_focal_nodes) > 0) {
  stop(paste("Critical Error: Focal nodes failed sample size criterion:", paste(ineligible_focal_nodes, collapse = ", ")))
}

# 3. Aggregate long format person-period data into grouped binomial format
# Losslessly compresses the dataset for rapid generalized linear modeling
hazard_by_node <- person_period_data %>%
  group_by(time_step, node_id) %>%
  summarise(
    events = sum(event, na.rm = TRUE),
    trials = n(),
    non_events = trials - events,
    .groups = "drop"
  )

# 4. Function: Fit a One-vs-Rest grouped binomial GLM for a target node
# Evaluates the excess hazard of a specific node relative to the prevailing baseline retention trend
fit_one_node <- function(target_node_name) {
  
  dat <- hazard_by_node %>%
    mutate(
      target = as.integer(node_id == target_node_name)
    ) %>%
    group_by(time_step, target) %>%
    summarise(
      events = sum(events, na.rm = TRUE),
      trials = sum(trials, na.rm = TRUE),
      non_events = trials - events,
      .groups = "drop"
    ) %>%
    # Scale time by 10 to ensure numerical stability and proper convergence of polynomial terms
    mutate(
      time_10 = time_step / 10,
      time_10_sq = time_10^2
    )

  fit <- glm(
    cbind(events, non_events) ~ time_10 + time_10_sq + target,
    family = binomial(link = "logit"),
    data = dat
  )

  coefs <- summary(fit)$coefficients
  est <- coefs["target", "Estimate"]
  se  <- coefs["target", "Std. Error"]
  p   <- coefs["target", "Pr(>|z|)"]

  tibble(
    node_id = target_node_name,
    Odds_Ratio = exp(est),
    conf.low = exp(est - 1.96 * se),
    conf.high = exp(est + 1.96 * se),
    p.value = p
  )
}

# 5. Execute models across all eligible nodes and apply False Discovery Rate (FDR) correction
all_eligible_node_results <- map_dfr(eligible_nodes, fit_one_node) %>%
  left_join(node_risk_table, by = "node_id") %>%
  mutate(
    # Apply Benjamini-Hochberg procedure across the entire family of eligible tests
    p.adj_all_eligible = p.adjust(p.value, method = "BH"),
    dropout_rate_percent = dropout_rate * 100
  )

# 6. Filter results to display only the focal nodes while retaining the globally corrected p-values
node_test_results <- all_eligible_node_results %>%
  filter(node_id %in% focal_nodes_to_display) %>%
  mutate(
    significance_all_eligible = case_when(
      p.adj_all_eligible < 0.001 ~ "***",
      p.adj_all_eligible < 0.01  ~ "**",
      p.adj_all_eligible < 0.05  ~ "*",
      TRUE ~ "ns"
    )
  ) %>%
  arrange(desc(Odds_Ratio)) %>%
  select(
    node_id, at_risk_n, dropouts, dropout_rate_percent, dropout_share, 
    Odds_Ratio, conf.low, conf.high, p.adj_all_eligible, significance_all_eligible
  )

print(node_test_results, n = Inf, width = Inf)
```

## Appendix B
```{r}
format_p <- function(x) ifelse(x < .001, "<.001", sprintf("%.3f", x))

table_b1 <- all_eligible_node_results %>%
  filter(node_id %in% focal_nodes_to_display) %>%
  left_join(
    node_metadata %>% select(node_id, route_simplified) %>% distinct(),
    by = "node_id"
  ) %>%
  mutate(
    location = case_when(
      node_id == "ConsentToSurvey" | str_starts(node_id, "W") |
        node_id == "Q1_DogNumber" ~ "Pre-route/common",
      route_simplified == "owner_main" ~ "Dog-owner",
      route_simplified == "repeated_dogs_loop" ~ "Repeated-dog",
      route_simplified == "non_owner_exit" ~ "Non-owner",
      TRUE ~ NA_character_
    )
  ) %>%
  arrange(desc(Odds_Ratio)) %>%
  transmute(
    Location = location,
    Node = str_replace_all(node_id, "_", "_\n"),
    `At risk` = scales::comma(at_risk_n),
    Breakoffs = scales::comma(dropouts),
    `Empirical hazard` = scales::percent(dropout_rate, accuracy = 0.01),
    `Time-adjusted OR (95% CI)` = sprintf(
      "%.3f (%.3f–%.3f)",
      Odds_Ratio,
      conf.low,
      conf.high
    ),
    `p-value (raw / BH)` = paste0(
      format_p(p.value),
      " / ",
      format_p(p.adj_all_eligible)
    )
  )

stopifnot(
  nrow(table_b1) == length(focal_nodes_to_display),
  !anyNA(table_b1$Location)
)

table_b1_ft <- flextable(table_b1) %>%
  set_caption(
    "Table B1. Time-adjusted one-versus-rest results for focal questionnaire nodes"
  ) %>%
  theme_booktabs() %>%
  font(fontname = "Times New Roman", part = "all") %>%
  fontsize(size = 7.5, part = "all") %>%
  bold(part = "header") %>%
  align(
    j = c(
      "At risk",
      "Breakoffs",
      "Empirical hazard",
      "Time-adjusted OR (95% CI)",
      "p-value (raw / BH)"
    ),
    align = "center",
    part = "all"
  ) %>%
  valign(valign = "top", part = "all") %>%
  padding(padding = 2, part = "all") %>%
  width(j = "Location", width = 0.90) %>%
  width(j = "Node", width = 1.25) %>%
  width(j = "At risk", width = 0.65) %>%
  width(j = "Breakoffs", width = 0.65) %>%
  width(j = "Empirical hazard", width = 0.75) %>%
  width(j = "Time-adjusted OR (95% CI)", width = 1.45) %>%
  width(j = "p-value (raw / BH)", width = 0.90) %>%
  set_table_properties(
    layout = "fixed",
    opts_word = list(split = FALSE, repeat_headers = TRUE)
  ) %>%
  add_footer_lines(
    paste(
      "Notes: Focal nodes comprise the union of the ten nodes with the",
      "largest breakoff counts and the ten nodes with the highest empirical",
      "hazards among nodes with at least 500 at-risk exposures.",
      "Odds ratios compare each focal node with all other questionnaire nodes",
      "after adjustment for linear and quadratic operational time.",
      "BH-adjusted p-values were calculated across all eligible nodes."
    )
  ) %>%
  italic(part = "footer") %>%
  fontsize(size = 7, part = "footer")

save_as_docx(
  table_b1_ft,
  path = "Appendix_Table_B1_Focal_Node_Models.docx",
  pr_section = prop_section(
    page_size = page_size(orient = "portrait"),
    page_margins = page_mar(
      top = 0.6,
      bottom = 0.6,
      left = 0.6,
      right = 0.6
    )
  )
)
```

## Full_Node_Level_Results
```{r}
full_node_results <- node_risk_table %>%
  left_join(
    all_eligible_node_results %>%
      select(
        node_id,
        Odds_Ratio,
        conf.low,
        conf.high,
        p.value,
        p.adj_all_eligible
      ),
    by = "node_id"
  ) %>%
  mutate(
    eligible_one_vs_rest = at_risk_n >= 500,
    exclusion_reason = if_else(
      eligible_one_vs_rest,
      NA_character_,
      "At-risk exposure count below 500"
    )
  ) %>%
  arrange(node_order)

stopifnot(nrow(full_node_results) == 141)

write_csv(
  full_node_results,
  "Full_Node_Level_Results.csv"
)
```


## Figure 4: Raw Attrition Hotspots
```{r}
# 1. Audit the person-period structure
# Each respondent should appear only once at each analytical node
duplicate_exposures <- person_period_data %>%
  count(ResponseId, node_id, name = "n_rows") %>%
  filter(n_rows > 1)

if (nrow(duplicate_exposures) > 0) {
  stop(
    "Duplicate respondent-node exposures were detected. ",
    "Check person_period_data before calculating node-level hazards."
  )
}

# One route classification per analytical node
node_route_lookup <- node_metadata %>%
  select(node_id, route_simplified) %>%
  distinct()

duplicate_route_labels <- node_route_lookup %>%
  count(node_id, name = "n_routes") %>%
  filter(n_routes > 1)

if (nrow(duplicate_route_labels) > 0) {
  stop(
    "Some node_ids have more than one route_simplified value ",
    "in node_metadata."
  )
}

# 3. Construct the node-level hotspot table
node_hotspots <- person_period_data %>%
  group_by(node_id) %>%
  summarise(
    # Number of respondents who encountered the node
    at_risk_n = n(),

    # Number who broke off at the node
    breakoff_n = sum(event == 1, na.rm = TRUE),

    .groups = "drop"
  ) %>%
  mutate(
    empirical_hazard = breakoff_n / at_risk_n
  ) %>%
  left_join(
    node_route_lookup,
    by = "node_id"
  ) %>%
  mutate(
    # Use metadata first, with node-name rules as a fallback
    route_group = case_when(
  route_simplified == "owner_main" ~ "Entry / owner route",
  route_simplified == "repeated_dogs_loop" ~ "Repeated-dog loop",
  route_simplified == "non_owner_exit" ~ "Non-owner",

  str_detect(as.character(node_id), "^E") ~ "Non-owner",
  str_detect(as.character(node_id), "^Q[2-5][0-9]{2}") ~
    "Repeated-dog loop",
  TRUE ~ "Entry / owner route"),

  route_group = factor(
  route_group,
  levels = c(
    "Entry / owner route",
    "Repeated-dog loop",
    "Non-owner")),

    node_label = as.character(node_id)
  )

# 4. Audit totals
total_locatable_breakoffs <- sum(
  node_hotspots$breakoff_n,
  na.rm = TRUE
)

cat("\n--- Figure 4 Audit ---\n")
cat(
  "Analytical nodes:",
  nrow(node_hotspots),
  "\n"
)
cat(
  "Total node exposures:",
  comma(sum(node_hotspots$at_risk_n)),
  "\n"
)
cat(
  "Total locatable breakoffs:",
  comma(total_locatable_breakoffs),
  "\n"
)

# Each breakoff respondent should contribute exactly one event
stopifnot(
  total_locatable_breakoffs ==
    sum(person_period_data$event, na.rm = TRUE)
)

# Expected final-sample value
if (total_locatable_breakoffs != 95034) {
  warning(
    "The total number of locatable breakoffs is ",
    comma(total_locatable_breakoffs),
    ", rather than the expected final value of 95,034. ",
    "Check that the latest person_period_data object is being used."
  )
}

# 5. Select the two Top 10 sets

# Panel A: largest absolute number of breakoffs
top_count_nodes <- node_hotspots %>%
  filter(breakoff_n > 0) %>%
  mutate(
    breakoff_share =
      breakoff_n / total_locatable_breakoffs
  ) %>%
  slice_max(
    order_by = breakoff_n,
    n = 10,
    with_ties = FALSE
  ) %>%
  arrange(breakoff_n) %>%
  mutate(
    node_label = factor(
      node_label,
      levels = node_label
    ),
    count_annotation = paste0(
      comma(breakoff_n),
      "  (",
      percent(breakoff_share, accuracy = 0.1),
      ")"
    )
  )

# Panel B: largest conditional hazards among stable risk sets
top_hazard_nodes <- node_hotspots %>%
  filter(
    at_risk_n >= 500,
    breakoff_n > 0
  ) %>%
  slice_max(
    order_by = empirical_hazard,
    n = 10,
    with_ties = FALSE
  ) %>%
  arrange(empirical_hazard) %>%
  mutate(
    node_label = factor(
      node_label,
      levels = node_label
    ),
    hazard_annotation = paste0(
      percent(empirical_hazard, accuracy = 0.1),
      "  (n at risk = ",
      comma(at_risk_n),
      ")"
    )
  )

cat("\nTop 10 by breakoff count:\n")
print(
  top_count_nodes %>%
    select(
      node_id,
      route_group,
      at_risk_n,
      breakoff_n,
      breakoff_share,
      empirical_hazard
    )
)

cat("\nTop 10 by conditional hazard:\n")
print(
  top_hazard_nodes %>%
    select(
      node_id,
      route_group,
      at_risk_n,
      breakoff_n,
      empirical_hazard
    )
)
```


```{r}
# 6. Common colour scheme
route_colours <- c(
  "Entry / owner route" = "#2C7FB8",
  "Repeated-dog loop" = "#41AE76",
  "Non-owner" = "#D95F0E"
)

common_theme <- theme_minimal(base_size = 11.5) +
  theme(
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.y = element_blank(),
    axis.text.y = element_text(
      colour = "#273746",
      size = 9.5,
      lineheight = 0.95
    ),
    axis.text.x = element_text(
      colour = "#273746"
    ),
    plot.title = element_text(
      face = "bold",
      size = 13
    ),
    plot.subtitle = element_text(
      size = 9.5,
      colour = "#5D6D7E",
      margin = margin(b = 7)
    ),
    legend.position = "top",
    legend.justification = "left",
    legend.title = element_blank(),
    plot.margin = margin(
      t = 6,
      r = 40,
      b = 6,
      l = 6
    )
  )

# 7. Panel A: Top 10 by breakoff count

panel_a_hotspots <- ggplot(
  top_count_nodes,
  aes(
    x = breakoff_n,
    y = node_label,
    fill = route_group
  )
) +
  geom_col(
    width = 0.68,
    alpha = 0.92
  ) +
  geom_text(
    aes(label = count_annotation),
    hjust = -0.08,
    size = 3.2,
    colour = "#273746"
  ) +
  scale_fill_manual(
    values = route_colours,
    drop = FALSE
  ) +
  scale_x_continuous(
    labels = label_comma(),
    breaks = pretty_breaks(n = 5),
    expand = expansion(mult = c(0, 0.28))
  ) +
  coord_cartesian(clip = "off") +
  labs(
    title = "Highest-volume breakoff nodes",
    subtitle = "Breakoff count and percentage of 95,034 locatable breakoffs",
    x = "Number of breakoffs",
    fill = NULL
  ) +
  common_theme

# 8. Panel B: Top 10 by conditional hazard
panel_b_hotspots <- ggplot(
  top_hazard_nodes,
  aes(
    x = empirical_hazard,
    y = node_label,
    fill = route_group
  )
) +
  geom_col(
    width = 0.68,
    alpha = 0.92
  ) +
  geom_text(
    aes(label = hazard_annotation),
    hjust = -0.08,
    size = 3.15,
    colour = "#273746"
  ) +
  scale_fill_manual(
    values = route_colours,
    drop = FALSE
  ) +
  scale_x_continuous(
    labels = percent_format(accuracy = 1),
    breaks = pretty_breaks(n = 5),
    expand = expansion(mult = c(0, 0.42))
  ) +
  coord_cartesian(clip = "off") +
  labs(
    title = "Highest-risk breakoff nodes",
    subtitle = "Conditional hazard among nodes with at least 500 respondents at risk",
    x = "Conditional breakoff hazard",
    fill = NULL
  ) +
  common_theme

# 9. Combine panels
panel_a_hotspots <- panel_a_hotspots +
  theme(legend.position = "none")

panel_b_hotspots <- panel_b_hotspots +
  guides(
    fill = guide_legend(
      title = NULL,
      nrow = 1,
      byrow = TRUE
    )
  ) +
  theme(legend.position = "bottom")

figure4_raw_attrition_hotspots <-
  panel_a_hotspots /
  panel_b_hotspots +
  patchwork::plot_layout(
    heights = c(1, 1)
  ) +
  patchwork::plot_annotation(
    tag_levels = "A",
    theme = theme(
      plot.tag = element_text(face = "bold", size = 13),
      plot.margin = margin(8, 12, 8, 12)
    )
  )

print(figure4_raw_attrition_hotspots)

# 10. Export dissertation-quality versions
# High-resolution PNG for Word
ggsave(
  filename = "figure4-raw-attrition-hotspots.png",
  plot = figure4_raw_attrition_hotspots,
  width = 7.2,
  height = 8.4,
  units = "in",
  dpi = 600,
  bg = "white"
)
```




# Step 6A: Fixed Setup, Metadata Integration, and Data Aggregation
```{r}
# Prepares the aggregated grouped-binomial dataset for question-design feature modeling
# 1. Define statistical helper functions
to_binary <- function(x, variable_name) {
  x_chr <- str_to_lower(str_squish(as.character(x)))
  result <- case_when(
    is.na(x) ~ NA_integer_,
    x_chr %in% c("1", "yes", "true", "y") ~ 1L,
    x_chr %in% c("0", "no", "false", "n") ~ 0L,
    TRUE ~ NA_integer_
  )
  invalid_values <- unique(as.character(x)[!is.na(x) & is.na(result)])
  if (length(invalid_values) > 0) {
    stop(paste0("Unexpected values in ", variable_name, ": ", paste(invalid_values, collapse = ", ")))
  }
  result
}

check_model_collinearity <- function(model, model_name) {
  if (!isTRUE(model$converged)) {
    warning(paste(model_name, "did not converge."))
  }
  design_matrix <- model.matrix(model)
  if (qr(design_matrix)$rank < ncol(design_matrix)) {
    warning(paste(model_name, "contains perfectly collinear terms."))
  }
}

dispersion_ratio <- function(model) {
  sum(residuals(model, type = "pearson")^2) / df.residual(model)
}

# Extract a dispersion-adjusted nested-model F-test
extract_f_test <- function(smaller_model,
                           larger_model,
                           comparison_name) {

  test_output <- anova(
    smaller_model,
    larger_model,
    test = "F"
  )

  result_row <- test_output[nrow(test_output), ]

  tibble(
    comparison = comparison_name,
    df_added = result_row$Df,
    residual_df = result_row$`Resid. Df`,
    F_statistic = result_row$F,
    p_value = result_row$`Pr(>F)`
  )
}

extract_odds_ratios <- function(model, model_name) {
  # Utilize t-distribution critical values for quasibinomial models to adjust for overdispersion
  critical_value <- if (family(model)$family == "quasibinomial") {
    qt(0.975, df = df.residual(model))
  } else {
    qnorm(0.975)
  }

  broom::tidy(model) %>%
    filter(term != "(Intercept)") %>%
    mutate(
      Model = model_name,
      Odds_Ratio = exp(estimate),
      conf.low = exp(estimate - critical_value * std.error),
      conf.high = exp(estimate + critical_value * std.error),
      significance = case_when(
        p.value < 0.001 ~ "***",
        p.value < 0.01 ~ "**",
        p.value < 0.05 ~ "*",
        TRUE ~ "ns"
      )
    ) %>%
    select(Model, term, Odds_Ratio, conf.low, conf.high, p.value, significance)
}

print_model_summary <- function(model, model_name) {
  cat("\nResults for:", model_name, "\n")
  print(extract_odds_ratios(model, model_name), n = Inf, width = Inf)
}

# 2. Import and audit the refined node metadata
metadata_path <- "Survey_Node_Metadata_refined.csv"
node_metadata <- read_csv(metadata_path, show_col_types = FALSE)

# Generate node-level prompt-length tertiles for exploratory Model 4 variations
prompt_band_cutpoints <- quantile(
  node_metadata$prompt_word_count,
  probs = c(1 / 3, 2 / 3),
  na.rm = TRUE,
  type = 2,
  names = FALSE
)

node_metadata <- node_metadata %>%
  mutate(
    prompt_wc_band_tertile = cut(
      prompt_word_count,
      breaks = c(-Inf, prompt_band_cutpoints[1], prompt_band_cutpoints[2], Inf),
      labels = c("Low", "Medium", "High"),
      include.lowest = TRUE,
      right = TRUE
    ),
    prompt_wc_band_tertile = fct_relevel(factor(prompt_wc_band_tertile), "Low")
  )

# 3. Aggregate person-period observations and join metadata
hazard_data_base <- person_period_data %>%
  group_by(time_step, node_id) %>%
  summarise(
    events = sum(event, na.rm = TRUE),
    trials = n(),
    .groups = "drop"
  )

model_2_data <- hazard_data_base %>%
  left_join(node_metadata, by = "node_id") %>%
  transmute(
    node_id,
    events = as.numeric(events),
    trials = as.numeric(trials),
    time_5 = as.numeric(time_step) / 5,
    route_simplified = fct_relevel(factor(route_simplified), "owner_main"),
    has_text_entry = to_binary(has_text_entry, "has_text_entry"),
    financial_sensitivity = to_binary(financial_sensitivity, "financial_sensitivity"),
    privacy_level = factor(privacy_level, levels = c("Low", "Medium", "High")),
    is_long_choice = to_binary(is_long_choice, "is_long_choice"),
    prompt_wc_10 = as.numeric(as.character(prompt_wc_10)),
    prompt_wc_band_tertile
  )

# 4. Restrict to complete cases and center the temporal baseline
model_common_raw <- model_2_data %>%
  drop_na(
    node_id, events, trials, time_5, route_simplified, has_text_entry,
    financial_sensitivity, privacy_level, is_long_choice,
    prompt_wc_10, prompt_wc_band_tertile
  )

time_5_mean <- weighted.mean(model_common_raw$time_5, w = model_common_raw$trials, na.rm = TRUE)

model_common_raw <- model_common_raw %>%
  mutate(
    time_5_c = time_5 - time_5_mean,
    time_5_c_sq = time_5_c^2
  )

# 5. Build the final aggregated grouped-binomial matrix
grouping_vars <- c(
  "time_5_c", "time_5_c_sq", "route_simplified", "has_text_entry",
  "financial_sensitivity", "privacy_level", "is_long_choice",
  "prompt_wc_10", "prompt_wc_band_tertile"
)

model_compare_agg <- model_common_raw %>%
  group_by(across(all_of(grouping_vars))) %>%
  summarise(
    events = sum(events, na.rm = TRUE),
    trials = sum(trials, na.rm = TRUE),
    non_events = trials - events,
    .groups = "drop"
  ) %>%
  filter(trials > 0) %>%
  mutate(across(where(is.factor), fct_drop))

cat("Final aggregated grouped-binomial rows:", nrow(model_compare_agg), "\n")
```


# Step 6B: Four-Stage Nested Model Specification and Fitting
```{r}
# Establishes the progressive logistic regression models to evaluate overarching design mechanisms

# 1. Define formulas for the four progressive models
model_formulas <- list(
  # Model 1: Baseline non-linear temporal fatigue
  "Model 1" = formula(cbind(events, non_events) ~ time_5_c + time_5_c_sq),
  
  # Model 2: Controls for structural routing disparities
  "Model 2" = formula(cbind(events, non_events) ~ time_5_c + time_5_c_sq + route_simplified),
  
  # Model 3: Core mechanism model testing UX friction and psychological resistance
  "Model 3" = formula(cbind(events, non_events) ~ time_5_c + time_5_c_sq + route_simplified + 
                      has_text_entry + financial_sensitivity + privacy_level),
  
  # Model 4: Extended burden model including scanning and reading effort
  "Model 4" = formula(cbind(events, non_events) ~ time_5_c + time_5_c_sq + route_simplified + 
                      has_text_entry + financial_sensitivity + privacy_level + 
                      prompt_wc_10 + is_long_choice)
                      
  # NOTE: To test the categorical reading burden in Model 4, simply replace 'prompt_wc_10' 
  # with 'prompt_wc_band_tertile' in the formula above.
)

# 2. Fit models using Quasibinomial distribution to adjust for unobserved heterogeneity (overdispersion)
models_quasi <- map(
  model_formulas,
  ~ glm(
    formula = .x,
    family = quasibinomial(link = "logit"),
    data = model_compare_agg
  )
)

# 3. Execute collinearity audits
walk2(models_quasi, names(models_quasi), check_model_collinearity)

# 4. Output the definitive results for Model 3 (Core) and Model 4 (Extended)
print_model_summary(models_quasi[["Model 3"]], "Model 3: Core Features")
print_model_summary(models_quasi[["Model 4"]], "Model 4: Extended Burden")

# 5. Evaluate Overdispersion (Unobserved Heterogeneity)
cat("\nOverdispersion ratio for Model 4:", dispersion_ratio(models_quasi[["Model 4"]]), "\n")
```


# Step 6C: Model 1 & 2 Outputs, Nested ANOVA, and Fit Statistics
```{r}
cat("\n--- 1. Output for Model 1 (Time Baseline) and Model 2 (Route Control) ---\n")
print_model_summary(models_quasi[["Model 1"]], "Model 1: Time Baseline")
print_model_summary(models_quasi[["Model 2"]], "Model 2: Route Control")

cat("\n--- 2. ANOVA F-Test for Nested Models ---\n")
# Note: For Quasibinomial models, we MUST use test = "F" instead of "Chisq" 
# because the dispersion parameter is estimated rather than fixed at 1.
cat("\nDoes Model 4 (Extended Burden) significantly improve upon Model 3 (Core Features)?\n")
anova_m3_m4 <- anova(models_quasi[["Model 3"]], models_quasi[["Model 4"]], test = "F")
print(anova_m3_m4)

cat("\n--- 3. Model Fit Statistics for Thesis Reporting (Model 4) ---\n")
# Extract exact degrees of freedom and deviance statistics for your methodology/results tables
mod4 <- models_quasi[["Model 4"]]

fit_stats <- tibble(
  Statistic = c(
    "Aggregated Rows (Observations in GLM)",
    "Total Analyzed Trials (Risk Set)",
    "Total Analyzed Events (Dropouts)",
    "Null Deviance",
    "Null Degrees of Freedom",
    "Residual Deviance",
    "Residual Degrees of Freedom",
    "Estimated Dispersion Parameter (Phi)"
  ),
  Value = c(
    nobs(mod4),
    sum(model_compare_agg$trials),
    sum(model_compare_agg$events),
    round(mod4$null.deviance, 2),
    mod4$df.null,
    round(mod4$deviance, 2),
    mod4$df.residual,
    round(dispersion_ratio(mod4), 3)
  )
)

print(fit_stats, n = Inf)
```


## Model 4 Alternative: Categorical Reading Burden
```{r}
burden_data <- model_common_raw %>%
  left_join(
    node_metadata %>%
      select(node_id, option_wc_10, total_visible_wc_10) %>%
      distinct(),
    by = "node_id"
  ) %>%
  mutate(
    option_wc_10 = as.numeric(option_wc_10),
    total_visible_wc_10 = as.numeric(total_visible_wc_10),
    non_events = trials - events
  ) %>%
  drop_na(option_wc_10, total_visible_wc_10)

stopifnot(
  sum(burden_data$trials) == sum(model_common_raw$trials),
  sum(burden_data$events) == sum(model_common_raw$events)
)

burden_base <- glm(
  cbind(events, non_events) ~
    time_5_c + time_5_c_sq + route_simplified +
    has_text_entry + financial_sensitivity + privacy_level,
  family = quasibinomial("logit"),
  data = burden_data
)

burden_models <- list(
  "Continuous prompt words" = update(
    burden_base,
    . ~ . + prompt_wc_10 + is_long_choice
  ),
  "Prompt-length tertiles" = update(
    burden_base,
    . ~ . + prompt_wc_band_tertile + is_long_choice
  ),
  "Total visible words" = update(
    burden_base,
    . ~ . + total_visible_wc_10 + is_long_choice
  ),
  "Prompt and option words" = update(
    burden_base,
    . ~ . + prompt_wc_10 + option_wc_10 + is_long_choice
  )
)

burden_labels <- c(
  prompt_wc_10 = "Prompt words, per 10",
  prompt_wc_band_tertileMedium = "Medium prompt length",
  prompt_wc_band_tertileHigh = "High prompt length",
  total_visible_wc_10 = "Total visible words, per 10",
  option_wc_10 = "Visible option words, per 10"
)

burden_tests <- purrr::imap_dfr(
  burden_models,
  function(model, model_name) {
    test <- anova(burden_base, model, test = "F")
    result <- test[nrow(test), ]

    tibble(
      Model = model_name,
      df_added = result$Df,
      residual_df = result$`Resid. Df`,
      joint_F = result$F,
      joint_p = result$`Pr(>F)`,
      dispersion = dispersion_ratio(model)
    )
  }
)

c1_results <- purrr::imap_dfr(
  burden_models,
  function(model, model_name) {
    extract_odds_ratios(model, model_name) %>%
      filter(term %in% names(burden_labels))
  }
) %>%
  mutate(Coefficient = unname(burden_labels[term])) %>%
  left_join(burden_tests, by = "Model") %>%
  select(
    Model,
    Coefficient,
    Odds_Ratio,
    conf.low,
    conf.high,
    p.value,
    df_added,
    residual_df,
    joint_F,
    joint_p,
    dispersion
  )

print(c1_results, n = Inf, width = Inf)
```

## Appendix_Table_C1_Reading_Burden
```{r}
table_c1 <- c1_results %>%
  mutate(
    Specification = dplyr::case_when(
  Model == "Continuous prompt words" ~ "Continuous prompt",
  Model == "Prompt-length tertiles" ~ "Prompt tertiles",
  Model == "Total visible words" ~ "Total visible words",
  Model == "Prompt and option words" ~ "Decomposed words",
  TRUE ~ Model
),
    `OR (95% CI)` = sprintf(
      "%.3f (%.3f–%.3f)",
      Odds_Ratio,
      conf.low,
      conf.high
    ),
    `Coefficient p` = format_p(p.value),
    `Joint F (df)` = sprintf(
      "%.2f (%d, %d)",
      joint_F,
      as.integer(df_added),
      as.integer(residual_df)
    ),
    `Joint p` = format_p(joint_p),
    Dispersion = sprintf("%.1f", dispersion)
  ) %>%
  group_by(Specification) %>%
  mutate(
    `Joint F (df)` = if_else(
      row_number() == 1,
      `Joint F (df)`,
      ""
    ),
    `Joint p` = if_else(
      row_number() == 1,
      `Joint p`,
      ""
    ),
    Dispersion = if_else(
      row_number() == 1,
      Dispersion,
      ""
    )
  ) %>%
  ungroup() %>%
  select(
    Specification,
    Coefficient,
    `OR (95% CI)`,
    `Coefficient p`,
    `Joint F (df)`,
    `Joint p`,
    Dispersion
  )

table_c1_ft <- flextable(table_c1) %>%
  set_caption(
    "Table C1. Alternative reading-burden specifications"
  ) %>%
  set_header_labels(
    `OR (95% CI)` = "OR\n(95% CI)",
    `Coefficient p` = "Coefficient\np-value",
    `Joint F (df)` = "Joint F\n(df)",
    `Joint p` = "Joint\np-value"
  ) %>%
  theme_booktabs() %>%
  font(fontname = "Times New Roman", part = "all") %>%
  fontsize(size = 7.5, part = "all") %>%
  bold(part = "header") %>%
  align(
    j = c(
      "OR (95% CI)",
      "Coefficient p",
      "Joint F (df)",
      "Joint p",
      "Dispersion"
    ),
    align = "center",
    part = "all"
  ) %>%
  valign(valign = "top", part = "all") %>%
  padding(padding = 2, part = "all") %>%
  width(j = "Specification", width = 1.05) %>%
  width(j = "Coefficient", width = 1.25) %>%
  width(j = "OR (95% CI)", width = 1.25) %>%
  width(j = "Coefficient p", width = 0.70) %>%
  width(j = "Joint F (df)", width = 1.00) %>%
  width(j = "Joint p", width = 0.60) %>%
  width(j = "Dispersion", width = 0.70) %>%
  set_table_properties(
    layout = "fixed",
    opts_word = list(
      split = FALSE,
      repeat_headers = TRUE
    )
  ) %>%
  add_footer_lines(
    paste(
      "Notes: Odds ratios are reported with t-based 95% confidence",
      "intervals. Low prompt length is the reference category for the",
      "tertile specification. Each joint F-test compares the corresponding",
      "reading-burden specification plus long-choice status with the core",
      "Model 3 specification. A significant joint test therefore does not",
      "imply that every individual word-count coefficient is significant.",
      "All specifications were estimated using the same node-time dataset."
    )
  ) %>%
  italic(part = "footer") %>%
  fontsize(size = 7, part = "footer")

save_as_docx(
  table_c1_ft,
  path = "Appendix_Table_C1_Reading_Burden.docx",
  pr_section = prop_section(
    page_size = page_size(orient = "portrait"),
    page_margins = page_mar(
      top = 0.6,
      bottom = 0.6,
      left = 0.6,
      right = 0.6
    )
  )
)
```


## Test cognitive_burden_score and topic_category
```{r}
# 1. Add the two metadata variables to the existing Model 4 data
metadata_test_raw <- model_common_raw %>%
  left_join(
    node_metadata %>%
      select(
        node_id,
        cognitive_burden_score,
        topic_category
      ) %>%
      distinct(),
    by = "node_id"
  ) %>%
  mutate(
    cognitive_burden_score = factor(
      cognitive_burden_score,
      levels = c(1, 2, 3)
    ),
    topic_category = fct_relevel(
      factor(topic_category),
      "Other"
    )
  ) %>%
  drop_na(
    cognitive_burden_score,
    topic_category
  )

# Check whether observations were lost
cat(
  "Rows before metadata addition:",
  nrow(model_common_raw),
  "\nRows retained:",
  nrow(metadata_test_raw),
  "\n"
)

# 2. Re-aggregate using the same common sample
metadata_test_agg <- metadata_test_raw %>%
  group_by(
    time_5_c,
    time_5_c_sq,
    route_simplified,
    has_text_entry,
    financial_sensitivity,
    privacy_level,
    prompt_wc_10,
    is_long_choice,
    cognitive_burden_score,
    topic_category
  ) %>%
  summarise(
    events = sum(events, na.rm = TRUE),
    trials = sum(trials, na.rm = TRUE),
    non_events = trials - events,
    .groups = "drop"
  ) %>%
  filter(trials > 0) %>%
  mutate(
    across(where(is.factor), fct_drop)
  )

# 3. Refit Model 4 on exactly the same metadata-complete sample
mod4_metadata_base <- glm(
  cbind(events, non_events) ~
    time_5_c +
    time_5_c_sq +
    route_simplified +
    has_text_entry +
    financial_sensitivity +
    privacy_level +
    prompt_wc_10 +
    is_long_choice,
  family = quasibinomial(link = "logit"),
  data = metadata_test_agg
)

# 4. Add cognitive burden score
mod4_cognitive <- update(
  mod4_metadata_base,
  . ~ . + cognitive_burden_score
)

# 5. Add topic category
mod4_topic <- update(
  mod4_metadata_base,
  . ~ . + topic_category
)

# 6. Add both variables
mod4_cognitive_topic <- update(
  mod4_metadata_base,
  . ~ . + cognitive_burden_score + topic_category
)

# 7. Check convergence and perfect collinearity
check_model_collinearity(
  mod4_cognitive,
  "Model 4 + cognitive burden"
)

check_model_collinearity(
  mod4_topic,
  "Model 4 + topic category"
)

check_model_collinearity(
  mod4_cognitive_topic,
  "Model 4 + cognitive burden + topic"
)

# 8. Overall F-tests
cat("\n--- Cognitive burden added to Model 4 ---\n")
print(
  anova(
    mod4_metadata_base,
    mod4_cognitive,
    test = "F"
  )
)

cat("\n--- Topic category added to Model 4 ---\n")
print(
  anova(
    mod4_metadata_base,
    mod4_topic,
    test = "F"
  )
)

cat("\n--- Cognitive burden after controlling for topic ---\n")
print(
  anova(
    mod4_topic,
    mod4_cognitive_topic,
    test = "F"
  )
)

cat("\n--- Topic category after controlling for cognitive burden ---\n")
print(
  anova(
    mod4_cognitive,
    mod4_cognitive_topic,
    test = "F"
  )
)

# 9. Display only the new coefficients as ORs
cognitive_results <- extract_odds_ratios(
  mod4_cognitive,
  "Model 4 + cognitive burden"
) %>%
  filter(str_detect(term, "^cognitive_burden_score"))

topic_results <- extract_odds_ratios(
  mod4_topic,
  "Model 4 + topic category"
) %>%
  filter(str_detect(term, "^topic_category"))

combined_results <- extract_odds_ratios(
  mod4_cognitive_topic,
  "Model 4 + both"
) %>%
  filter(
    str_detect(
      term,
      "^cognitive_burden_score|^topic_category"
    )
  )

bind_rows(
  cognitive_results,
  topic_results,
  combined_results
) %>%
  print(n = Inf, width = Inf)

# 10. Dispersion ratios
cat(
  "\nModel 4 dispersion:",
  round(dispersion_ratio(mod4_metadata_base), 3),
  "\nCognitive model dispersion:",
  round(dispersion_ratio(mod4_cognitive), 3),
  "\nTopic model dispersion:",
  round(dispersion_ratio(mod4_topic), 3),
  "\nCombined model dispersion:",
  round(dispersion_ratio(mod4_cognitive_topic), 3),
  "\n"
)
```


## c3_cognitive_coefficients
```{r}
c3_tests <- bind_rows(
  extract_f_test(
    mod4_metadata_base,
    mod4_cognitive,
    "Cognitive burden added to Model 4"
  ) %>%
    mutate(dispersion = dispersion_ratio(mod4_cognitive)),

  extract_f_test(
    mod4_metadata_base,
    mod4_topic,
    "Topic category added to Model 4"
  ) %>%
    mutate(dispersion = dispersion_ratio(mod4_topic)),

  extract_f_test(
    mod4_topic,
    mod4_cognitive_topic,
    "Cognitive burden after topic"
  ) %>%
    mutate(dispersion = dispersion_ratio(mod4_cognitive_topic)),

  extract_f_test(
    mod4_cognitive,
    mod4_cognitive_topic,
    "Topic category after cognitive burden"
  ) %>%
    mutate(dispersion = dispersion_ratio(mod4_cognitive_topic))
)

c3_cognitive_coefficients <- extract_odds_ratios(
  mod4_cognitive_topic,
  "Model 4 + cognitive burden + topic"
) %>%
  filter(str_detect(term, "^cognitive_burden_score")) %>%
  select(
    term,
    Odds_Ratio,
    conf.low,
    conf.high,
    p.value
  )

print(c3_tests, n = Inf, width = Inf)
print(c3_cognitive_coefficients, n = Inf, width = Inf)
```


## Appendix_Table_C3_Cognitive_Topic_Extensions
```{r}
table_c3 <- c3_tests %>%
  slice_head(n = 4) %>%
  transmute(
    Comparison = comparison,
    `df added` = as.integer(df_added),
    `Residual df` = as.integer(residual_df),
    `F statistic` = sprintf("%.2f", F_statistic),
    `p-value` = format_p(p_value),
    Dispersion = sprintf("%.1f", dispersion)
  )

table_c3_ft <- flextable(table_c3) %>%
  set_caption(
    "Table C3. Joint tests of cognitive-burden and topic-category extensions"
  ) %>%
  theme_booktabs() %>%
  font(fontname = "Times New Roman", part = "all") %>%
  fontsize(size = 8.5, part = "all") %>%
  bold(part = "header") %>%
  align(
    j = c(
      "df added",
      "Residual df",
      "F statistic",
      "p-value",
      "Dispersion"
    ),
    align = "center",
    part = "all"
  ) %>%
  valign(valign = "center", part = "all") %>%
  width(j = "Comparison", width = 3.4) %>%
  width(j = "df added", width = 0.65) %>%
  width(j = "Residual df", width = 0.75) %>%
  width(j = "F statistic", width = 0.75) %>%
  width(j = "p-value", width = 0.65) %>%
  width(j = "Dispersion", width = 0.75) %>%
  set_table_properties(
    layout = "fixed",
    width = 1,
    opts_word = list(
      split = FALSE,
      repeat_headers = TRUE
    )
  ) %>%
  add_footer_lines(
    paste(
      "Notes: Each row reports a nested F-test comparing the indicated",
      "extended quasibinomial model with its reduced counterpart. Dispersion",
      "refers to the larger model. Individual cognitive-burden contrasts are",
      "not reported because the highest-burden category produced an unstable",
      "coefficient with an unbounded confidence interval. These block tests",
      "are interpreted as exploratory tests of joint contribution rather than",
      "evidence of specific category-level effects."
    )
  ) %>%
  italic(part = "footer") %>%
  fontsize(size = 7.5, part = "footer")

save_as_docx(
  table_c3_ft,
  path = "Appendix_Table_C3_Cognitive_Topic_Extensions.docx",
  pr_section = prop_section(
    page_size = page_size(orient = "portrait"),
    page_margins = page_mar(
      top = 0.6,
      bottom = 0.6,
      left = 0.6,
      right = 0.6
    )
  )
)
```


```{r}
# 1. Extract ORs and t-based 95% CIs from quasibinomial models
extract_quasi_results <- function(model, model_name) {

  coef_table <- as.data.frame(
    summary(model)$coefficients
  )

  critical_value <- qt(
    0.975,
    df = df.residual(model)
  )

  tibble(
    model = model_name,
    term = rownames(coef_table),
    estimate = coef_table[, "Estimate"],
    std_error = coef_table[, "Std. Error"],
    p_value = coef_table[, ncol(coef_table)]
  ) %>%
    mutate(
      conf_low_log =
        estimate - critical_value * std_error,
      conf_high_log =
        estimate + critical_value * std_error,

      odds_ratio = exp(estimate),
      conf_low = exp(conf_low_log),
      conf_high = exp(conf_high_log),

      significance = case_when(
        p_value < 0.001 ~ "***",
        p_value < 0.01  ~ "**",
        p_value < 0.05  ~ "*",
        TRUE            ~ ""
      ),

      estimate_ci = paste0(
        sprintf("%.3f", odds_ratio),
        " [",
        sprintf("%.3f", conf_low),
        ", ",
        sprintf("%.3f", conf_high),
        "]",
        significance
      )
    )
}

# Only the four primary models
main_models <- models_quasi[
  c("Model 1", "Model 2", "Model 3", "Model 4")
]

table3_long <- purrr::imap_dfr(
  main_models,
  ~ extract_quasi_results(.x, .y)
)

# 2. Reader-friendly variable labels

term_labels <- c(
  "time_5_c" =
    "Operational time (centred 5-node units)",

  "time_5_c_sq" =
    "Operational time squared",

  "route_simplifiedrepeated_dogs_loop" =
    "Repeated-dog loop",

  "route_simplifiednon_owner_exit" =
    "Non-owner route",

  "has_text_entry" =
    "Text entry required",

  "financial_sensitivity" =
    "Financially sensitive content",

  "privacy_levelMedium" =
    "Privacy level: Medium",

  "privacy_levelHigh" =
    "Privacy level: High",

  "prompt_wc_10" =
    "Prompt length (per 10 additional words)",

  "is_long_choice" =
    "Long choice set"
)

term_order <- names(term_labels)

# 3. Convert to the wide Table 3 format
table3_display <- table3_long %>%
  filter(term %in% term_order) %>%
  mutate(
    predictor = unname(term_labels[term]),
    row_order = match(term, term_order),
    model = factor(
      model,
      levels = c(
        "Model 1",
        "Model 2",
        "Model 3",
        "Model 4"
      )
    )
  ) %>%
  arrange(row_order, model) %>%
  select(
    row_order,
    Predictor = predictor,
    model,
    estimate_ci
  ) %>%
  pivot_wider(
    names_from = model,
    values_from = estimate_ci,
    values_fill = "\u2014"
  ) %>%
  arrange(row_order) %>%
  select(-row_order)

print(table3_display)
```

## table 3
```{r}
table3_ft <- flextable(table3_display) %>%
  set_caption(
    caption = paste0(
      "Table 3. Progressive quasibinomial discrete-time ",
      "hazard models of questionnaire breakoff"
    )
  ) %>%
  theme_booktabs() %>%
  align(
    j = 1,
    align = "left",
    part = "all"
  ) %>%
  align(
    j = 2:5,
    align = "center",
    part = "all"
  ) %>%
  width(j = 1, width = 2.1) %>%
  width(j = 2:5, width = 1.05) %>%
  fontsize(size = 9.5, part = "body") %>%
  fontsize(size = 9.5, part = "header") %>%
  add_footer_lines(
    values = c(
      paste0(
        "Notes: Cells report odds ratios with t-based 95% ",
        "confidence intervals in brackets."
      ),
      paste0(
        "Reference categories: owner main route; low privacy; ",
        "no text entry; no financial sensitivity; and no long ",
        "choice set. Prompt length is measured per 10 additional words."
      ),
      "* p < .05; ** p < .01; *** p < .001."
    )
  ) %>%
  fontsize(size = 8, part = "footer") %>%
  italic(part = "footer") %>%
  set_table_properties(
    layout = "fixed",
    width = 1
  )

table3_ft

flextable::save_as_docx(
  table3_ft,
  path = "Table_3_Models_1_to_4.docx"
)

write.csv(
  table3_long,
  "Table_3_Full_Numerical_Results.csv",
  row.names = FALSE
)
```



## sequential F-tests
```{r}
# Confirm all models use the same analytical rows
stopifnot(
  length(unique(
    purrr::map_dbl(main_models, nobs)
  )) == 1
)

nested_f_tests <- bind_rows(
  extract_f_test(
    main_models[["Model 1"]],
    main_models[["Model 2"]],
    "Model 1 vs Model 2"
  ),
  extract_f_test(
    main_models[["Model 2"]],
    main_models[["Model 3"]],
    "Model 2 vs Model 3"
  ),
  extract_f_test(
    main_models[["Model 3"]],
    main_models[["Model 4"]],
    "Model 3 vs Model 4"
  )
)

print(nested_f_tests, n = Inf)
```



## figure 5
```{r}
# Figure 5: Adjusted ORs from final Model 4

figure5_terms <- c(
  "route_simplifiedrepeated_dogs_loop",
  "route_simplifiednon_owner_exit",
  "has_text_entry",
  "financial_sensitivity",
  "privacy_levelMedium",
  "privacy_levelHigh",
  "prompt_wc_10",
  "is_long_choice"
)

figure5_data <- extract_quasi_results(
  main_models[["Model 4"]],
  "Model 4"
) %>%
  filter(term %in% figure5_terms) %>%
  mutate(
    predictor = unname(term_labels[term]),

    # Determines the top-to-bottom order
    predictor = factor(
      predictor,
      levels = rev(
        unname(term_labels[figure5_terms])
      )
    )
  )

figure5_model4_adjusted_odds_ratios <- ggplot(
  figure5_data,
  aes(
    x = odds_ratio,
    y = predictor
  )
) +
  geom_vline(
    xintercept = 1,
    linetype = "dashed",
    linewidth = 0.6,
    colour = "#7F8C8D"
  ) +
  geom_segment(
    aes(
      x = conf_low,
      xend = conf_high,
      y = predictor,
      yend = predictor
    ),
    linewidth = 0.8,
    colour = "#2C7FB8"
  ) +
  geom_point(
    size = 3,
    shape = 21,
    fill = "#2C7FB8",
    colour = "white",
    stroke = 0.6
  ) +
  scale_x_log10(
    breaks = scales::log_breaks(n = 6),
    labels = scales::label_number(accuracy = 0.01)
  ) +
  labs(
    x = "Adjusted odds ratio (log scale)",
    y = NULL
  ) +
  theme_minimal(base_size = 11.5) +
  theme(
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text = element_text(colour = "#273746"),
    axis.text.y = element_text(size = 10),
    axis.title.x = element_text(
      margin = margin(t = 8)
    ),
    plot.margin = margin(
      t = 10,
      r = 15,
      b = 10,
      l = 10
    )
  )

print(figure5_model4_adjusted_odds_ratios)

ggsave(
  "figure5-model4-adjusted-odds-ratios.png",
  figure5_model4_adjusted_odds_ratios,
  width = 7.2,
  height = 4.8,
  units = "in",
  dpi = 600,
  bg = "white"
)
```


# Step 7: Route-Specific Heterogeneity and Descriptive Summary
```{r}
# Identify all nodes occurring before or at the route-defining question
q1_order <- node_order_tbl %>%
  filter(node_id == "Q1_DogNumber") %>%
  pull(node_order)

stopifnot(length(q1_order) == 1)

pre_route_nodes <- node_order_tbl %>%
  filter(node_order <= q1_order) %>%
  pull(node_id)

# Route-specific modelling dataset:
# retain only nodes occurring after route entry
route_model_raw <- model_common_raw %>%
  filter(
    !node_id %in% pre_route_nodes,
    route_simplified %in%
      c(
        "owner_main",
        "repeated_dogs_loop",
        "non_owner_exit"
      )
  )
```



## Owner route model
```{r}
owner_route_data <- route_model_raw %>%
  filter(
    route_simplified %in%
      c("owner_main", "repeated_dogs_loop")
  ) %>%
  group_by(
    time_5_c,
    time_5_c_sq,
    route_simplified,
    has_text_entry,
    financial_sensitivity,
    privacy_level,
    is_long_choice,
    prompt_wc_10
  ) %>%
  summarise(
    events = sum(events, na.rm = TRUE),
    trials = sum(trials, na.rm = TRUE),
    non_events = trials - events,
    .groups = "drop"
  ) %>%
  filter(trials > 0) %>%
  mutate(
    route_simplified = fct_relevel(
      factor(route_simplified),
      "owner_main"
    )
  )

model_owner_route <- glm(
  cbind(events, non_events) ~
    time_5_c +
    time_5_c_sq +
    route_simplified +
    has_text_entry +
    financial_sensitivity +
    privacy_level +
    is_long_choice +
    prompt_wc_10,
  family = quasibinomial("logit"),
  data = owner_route_data
)
```


## non-owner route model
```{r}
non_owner_route_data <- route_model_raw %>%
  filter(route_simplified == "non_owner_exit") %>%
  mutate(
    privacy_high =
      as.integer(privacy_level == "High")
  ) %>%
  group_by(
    time_5_c,
    time_5_c_sq,
    has_text_entry,
    financial_sensitivity,
    privacy_high,
    is_long_choice,
    prompt_wc_10
  ) %>%
  summarise(
    events = sum(events, na.rm = TRUE),
    trials = sum(trials, na.rm = TRUE),
    non_events = trials - events,
    .groups = "drop"
  ) %>%
  filter(trials > 0)

model_non_owner_route_final <- glm(
  cbind(events, non_events) ~
    time_5_c +
    time_5_c_sq +
    has_text_entry +
    financial_sensitivity +
    privacy_high +
    is_long_choice +
    prompt_wc_10,
  family = quasibinomial("logit"),
  data = non_owner_route_data
)
```



## table 5
```{r}
# Extract every coefficient from each route-specific model
extract_all_route_terms <- function(model, route_code) {

  critical_value <- qt(
    0.975,
    df = df.residual(model)
  )

  broom::tidy(model) %>%
    mutate(
      route = route_code,

      OR = exp(estimate),

      CI_low = exp(
        estimate -
          critical_value * std.error
      ),

      CI_high = exp(
        estimate +
          critical_value * std.error
      ),

      stars = case_when(
        p.value < 0.001 ~ "***",
        p.value < 0.01  ~ "**",
        p.value < 0.05  ~ "*",
        TRUE            ~ ""
      ),

      row_key = case_when(
        term == "(Intercept)" ~
          "intercept",

        term == "time_5_c" ~
          "time_linear",

        term == "time_5_c_sq" ~
          "time_quadratic",

        term ==
          "route_simplifiedrepeated_dogs_loop" ~
          "repeated_loop",

        term == "has_text_entry" ~
          "text_entry",

        term == "financial_sensitivity" ~
          "financial",

        route_code == "owner" &
          term == "privacy_levelMedium" ~
          "privacy_medium_low",

        route_code == "owner" &
          term == "privacy_levelHigh" ~
          "privacy_high_low",

        route_code == "non_owner" &
          term == "privacy_high" ~
          "privacy_high_lowmedium",

        term == "is_long_choice" ~
          "long_choice",

        term == "prompt_wc_10" ~
          "prompt_length",

        TRUE ~ NA_character_
      ),

      estimate_cell = sprintf(
  "%.3f [%.3f, %.3f]%s",
  OR,
  CI_low,
  CI_high,
  stars)
    )
}

# Combine the two final route-specific models
# and remove the intercept
route_terms_all <- bind_rows(
  extract_all_route_terms(
    model_owner_route,
    "owner"
  ),
  extract_all_route_terms(
    model_non_owner_route_final,
    "non_owner"
  )
) %>%
  filter(term != "(Intercept)")

# Check that all retained terms have been labelled
stopifnot(
  !any(is.na(route_terms_all$row_key))
)

# Row order and labels consistent with Table 5
route_row_specification <- tribble(
  ~row_order, ~row_key, ~Variable,

  1,
  "time_linear",
  "Operational time (centred 5-node units)",

  2,
  "time_quadratic",
  "Operational time squared",

  3,
  "repeated_loop",
  "Repeated-dog loop",

  4,
  "text_entry",
  "Text entry required",

  5,
  "financial",
  "Financially sensitive content",

  6,
  "privacy_medium_low",
  "Privacy level: Medium",

  7,
  "privacy_high_low",
  "Privacy level: High (ref: Low)",

  8,
  "privacy_high_lowmedium",
  "Privacy level: High (ref: Low/Medium)",

  9,
  "prompt_length",
  "Prompt length (per 10 additional words)",

  10,
  "long_choice",
  "Long choice set"
)

# Construct the coefficient section
route_table_full <- route_terms_all %>%
  select(
    row_key,
    route,
    estimate_cell
  ) %>%
  pivot_wider(
    names_from = route,
    values_from = estimate_cell
  ) %>%
  right_join(
    route_row_specification,
    by = "row_key"
  ) %>%
  arrange(row_order) %>%
  transmute(
    Variable,

    # Use an em dash when a term was not estimated
    owner = replace_na(owner, "—"),
    non_owner = replace_na(non_owner, "—")
  )

# Add model sample information
# Dispersion ratio is deliberately excluded
route_table_full <- bind_rows(
  route_table_full,

  tibble(
    Variable = c(
      "Respondent-node exposures",
      "Breakoff events"
    ),

    owner = c(
      format(
        sum(owner_route_data$trials),
        big.mark = ",",
        scientific = FALSE,
        trim = TRUE
      ),

      format(
        sum(owner_route_data$events),
        big.mark = ",",
        scientific = FALSE,
        trim = TRUE
      )
    ),

    non_owner = c(
      format(
        sum(non_owner_route_data$trials),
        big.mark = ",",
        scientific = FALSE,
        trim = TRUE
      ),

      format(
        sum(non_owner_route_data$events),
        big.mark = ",",
        scientific = FALSE,
        trim = TRUE
      )
    )
  )
)

# Format Table 5
Table_5_full <- flextable(
  route_table_full
) %>%
  set_header_labels(
    Variable = "Variable",
    owner = "Dog-owner route",
    non_owner = "Non-owner route"
  ) %>%
  set_caption(
    caption = paste(
      "Table 5. Route-specific quasibinomial",
      "discrete-time hazard models of questionnaire breakoff"
    )
  ) %>%
  theme_booktabs() %>%
  bold(part = "header") %>%
  align(
    j = 2:3,
    align = "center",
    part = "all"
  ) %>%
  valign(
    valign = "center",
    part = "all"
  ) %>%
  autofit() %>%
  add_footer_lines(
    values = c(
      paste(
        "Notes: Cells report adjusted odds ratios with",
        "t-based 95% confidence intervals."
      ),
      paste(
        "Em dashes indicate that the term was not estimated",
        "in the corresponding route-specific model."
      ),
      paste(
        "The dog-owner model used owner-main as the route",
        "reference and Low as the privacy reference category."
      ),
      paste(
        "The non-owner privacy coefficient compares High",
        "with the combined Low/Medium category."
      ),
      paste(
        "The non-owner high-privacy estimate is primarily",
        "supported by the postcode node and should be",
        "interpreted cautiously."
      ),
      "* p < .05, ** p < .01, *** p < .001."
    )
  ) %>%
  fontsize(
    size = 9,
    part = "footer"
  )

Table_5_full

save_as_docx(
  Table_5_full,
  path =
    "Table_5_Route_Specific_Adjusted_Associations_Full.docx"
)
```



## route traffic
```{r}
respondent_route_status <- raw_data %>%
  transmute(
    ResponseId,
    Finished,
    route_group = case_when(
      Q1_DogNumber == "I don't have a dog" ~
        "Non-Owner Route",

      Q1_DogNumber %in%
        c(
          "One",
          "Two",
          "Three",
          "Four",
          "Five or more (please specify)"
        ) ~
        "Dog Owner Route",

      TRUE ~ "Pre-route or undetermined"
    )
  )

route_traffic <- respondent_route_status %>%
  filter(
    route_group %in%
      c("Dog Owner Route", "Non-Owner Route")
  ) %>%
  group_by(route_group) %>%
  summarise(
    Total_Entrants = n(),
    Total_Dropouts =
      sum(Finished == FALSE, na.rm = TRUE),
    Dropout_Rate_Pct =
      100 * Total_Dropouts / Total_Entrants,
    .groups = "drop"
  )

print(route_traffic)
```



## graph
```{r}
# One unique metadata record per node
route_lookup <- node_metadata %>%
  select(
    node_id,
    route_simplified,
    topic_category
  ) %>%
  distinct()

stopifnot(
  anyDuplicated(route_lookup$node_id) == 0
)

# Attach the route indicated by each post-Q1 node
person_period_with_route <- person_period_data %>%
  left_join(
    route_lookup,
    by = "node_id"
  ) %>%
  filter(
    !node_id %in% pre_route_nodes
  ) %>%
  mutate(
    route_group = case_when(
      route_simplified ==
        "non_owner_exit" ~
        "Non-Owner Route",

      route_simplified %in%
        c(
          "owner_main",
          "repeated_dogs_loop"
        ) ~
        "Dog Owner Route",

      TRUE ~ NA_character_
    )
  ) %>%
  filter(!is.na(route_group))

# Node-level empirical risk and dropout concentration
route_node_risk <- person_period_with_route %>%
  group_by(
    route_group,
    node_id,
    topic_category
  ) %>%
  summarise(
    at_risk_n =
      n_distinct(ResponseId),

    dropouts =
      sum(event, na.rm = TRUE),

    empirical_hazard =
      dropouts / at_risk_n,

    .groups = "drop"
  ) %>%
  group_by(route_group) %>%
  arrange(
    desc(dropouts),
    .by_group = TRUE
  ) %>%
  mutate(
    volume_rank = row_number(),

    dropout_share_within_route =
      dropouts / sum(dropouts),

    cumulative_dropout_share =
      cumsum(
        dropout_share_within_route
      )
  ) %>%
  ungroup()

# Top five nodes within each route
route_hotspot_top5 <- route_node_risk %>%
  filter(volume_rank <= 5) %>%
  transmute(
    Route = route_group,
    Rank = volume_rank,
    Node = node_id,
    Topic = topic_category,
    `At risk` = at_risk_n,
    Dropouts = dropouts,

    `Empirical hazard (%)` =
      round(empirical_hazard * 100, 2),

    `Share of route dropouts (%)` =
      round(
        dropout_share_within_route * 100,
        2
      ),

    `Cumulative share (%)` =
      round(
        cumulative_dropout_share * 100,
        2
      )
  )

print(
  route_hotspot_top5,
  n = Inf,
  width = Inf
)
```



## Table 4: top10 table
```{r}
# Reader-facing descriptions for the ten hotspot nodes
hotspot_question_lookup <- tribble(
  ~Node, ~Question,

  "Q1.2_DogName",
  "Dog's name",

  "Q17.1_ServicesCutCoL",
  "Services cut due to cost of living",

  "Q13.2_HolidayAccommo",
  "Preferred holiday accommodation",

  "Q29_Postcode",
  "First part of postcode",

  "Q22_ImproveLife",
  "One thing that would improve life with the dog",

  "E2FutureDogOwner",
  "Hope to own a dog in the future",

  "E3_FutureDogSource",
  "Likely future sources for obtaining a dog",

  "E13_Postcode",
  "First part of postcode",

  "E8_GovRole",
  "Government role in dog welfare",

  "E3.1_NotRescue",
  "Reasons for not considering a rescue dog"
)

# Add readable question descriptions and format values
hotspot_table_base <- route_hotspot_top5 %>%
  left_join(
    hotspot_question_lookup,
    by = "Node"
  )

# Ensure that every Top-5 node has a description
stopifnot(
  !any(is.na(hotspot_table_base$Question))
)

hotspot_table_base <- hotspot_table_base %>%
  transmute(
    Route,

    Rank = as.character(Rank),

    `Node / question` =
      paste0(
        Node,
        " — ",
        Question
      ),

    `At risk` =
      format(
        `At risk`,
        big.mark = ",",
        scientific = FALSE,
        trim = TRUE
      ),

    Breakoffs =
      format(
        Dropouts,
        big.mark = ",",
        scientific = FALSE,
        trim = TRUE
      ),

    `Hazard (%)` =
      sprintf(
        "%.2f",
        `Empirical hazard (%)`
      ),

    `Route share (%)` =
      sprintf(
        "%.2f",
        `Share of route dropouts (%)`
      ),

    `Cumulative share (%)` =
      sprintf(
        "%.2f",
        `Cumulative share (%)`
      )
  )

# Check the route labels produced in the previous step
stopifnot(
  all(
    c(
      "Dog Owner Route",
      "Non-Owner Route"
    ) %in% unique(hotspot_table_base$Route)
  )
)

# Separate the two routes
owner_hotspots <- hotspot_table_base %>%
  filter(Route == "Dog Owner Route") %>%
  select(-Route)

non_owner_hotspots <- hotspot_table_base %>%
  filter(Route == "Non-Owner Route") %>%
  select(-Route)

# Create a panel-heading row
make_panel_row <- function(label) {
  tibble(
    Rank = label,
    `Node / question` = label,
    `At risk` = label,
    Breakoffs = label,
    `Hazard (%)` = label,
    `Route share (%)` = label,
    `Cumulative share (%)` = label
  )
}

# Combine the two panels into one table
table_4_data <- bind_rows(
  make_panel_row(
    "Panel A: Dog-owner route"
  ),
  owner_hotspots,

  make_panel_row(
    "Panel B: Non-owner route"
  ),
  non_owner_hotspots
)

# Positions of the two panel rows
panel_rows <- c(
  1,
  nrow(owner_hotspots) + 2
)

# Produce the final flextable
table_4_hotspots <- flextable(
  table_4_data
) %>%
  set_caption(
    caption = paste(
      "Table 4. Top five post-route breakoff",
      "hotspots by breakoff volume"
    )
  ) %>%
  theme_booktabs() %>%

  # Merge the cells across each panel heading
  merge_h(
    i = panel_rows,
    part = "body"
  ) %>%

  bold(
    i = panel_rows,
    part = "body"
  ) %>%

  bg(
    i = panel_rows,
    bg = "#EAF2F8",
    part = "body"
  ) %>%

  align(
    i = panel_rows,
    align = "left",
    part = "body"
  ) %>%

  bold(part = "header") %>%

  align(
    j = c(
      "Rank",
      "At risk",
      "Breakoffs",
      "Hazard (%)",
      "Route share (%)",
      "Cumulative share (%)"
    ),
    align = "center",
    part = "all"
  ) %>%

  valign(
    valign = "center",
    part = "all"
  ) %>%

  fontsize(
    size = 9,
    part = "all"
  ) %>%

  set_table_properties(
    layout = "fixed",
    width = 1
  ) %>%

  width(
    j = "Rank",
    width = 0.45
  ) %>%

  width(
    j = "Node / question",
    width = 2.35
  ) %>%

  width(
    j = "At risk",
    width = 0.75
  ) %>%

  width(
    j = "Breakoffs",
    width = 0.68
  ) %>%

  width(
    j = "Hazard (%)",
    width = 0.62
  ) %>%

  width(
    j = "Route share (%)",
    width = 0.72
  ) %>%

  width(
    j = "Cumulative share (%)",
    width = 0.78
  ) %>%

  add_footer_lines(
    values = paste(
      "Notes: Nodes were ranked by breakoff count rather",
      "than empirical hazard. At-risk counts represent",
      "respondents reaching each node. Route shares were",
      "calculated among locatable post-route breakoff events."
    )
  )

table_4_hotspots

save_as_docx(
  table_4_hotspots,
  path =
    "Table_4_Route_Specific_Top_5_Hotspots.docx"
)
```



## interaction test
```{r}
route_interaction_data <- route_model_raw %>%
  mutate(
    route_group = factor(
      if_else(
        route_simplified == "non_owner_exit",
        "Non-owner",
        "Owner"
      ),
      levels = c("Owner", "Non-owner")
    ),
    repeated_dog_loop =
      as.integer(
        route_simplified ==
          "repeated_dogs_loop"
      ),
    privacy_high =
      as.integer(privacy_level == "High")
  ) %>%
  group_by(
    time_5_c,
    time_5_c_sq,
    route_group,
    repeated_dog_loop,
    has_text_entry,
    financial_sensitivity,
    privacy_high,
    is_long_choice,
    prompt_wc_10
  ) %>%
  summarise(
    events = sum(events),
    trials = sum(trials),
    non_events = trials - events,
    .groups = "drop"
  ) %>%
  filter(trials > 0)

route_interaction_null <- glm(
  cbind(events, non_events) ~
    route_group * time_5_c +
    route_group * time_5_c_sq +
    repeated_dog_loop +
    has_text_entry +
    financial_sensitivity +
    privacy_high +
    is_long_choice +
    prompt_wc_10,
  family = quasibinomial("logit"),
  data = route_interaction_data
)

route_interaction_full <- update(
  route_interaction_null,
  . ~ . +
    route_group:financial_sensitivity +
    route_group:privacy_high +
    route_group:is_long_choice
)

route_interaction_joint_test <- anova(
  route_interaction_null,
  route_interaction_full,
  test = "F"
)

print(route_interaction_joint_test)
```


## C2_route_interaction_joint_test
```{r}
c2_results <- extract_odds_ratios(
  route_interaction_full,
  "Pooled route-interaction model"
) %>%
  filter(
    str_detect(term, "route_groupNon-owner") &
      str_detect(
        term,
        "financial_sensitivity|privacy_high|is_long_choice"
      )
  ) %>%
  mutate(
    Interaction = case_when(
      str_detect(term, "financial_sensitivity") ~
        "Non-owner route × financial sensitivity",
      str_detect(term, "privacy_high") ~
        "Non-owner route × high privacy",
      str_detect(term, "is_long_choice") ~
        "Non-owner route × long choice set"
    )
  ) %>%
  select(
    Interaction,
    Odds_Ratio,
    conf.low,
    conf.high,
    p.value
  )

print(c2_results, n = Inf, width = Inf)
print(route_interaction_joint_test)
```


## Appendix_Table_C2_Route_Interactions
```{r}
joint_result <- route_interaction_joint_test[2, ]

table_c2 <- c2_results %>%
  transmute(
    Interaction,
    `Ratio of ORs (95% CI)` = sprintf(
      "%.3f (%.3f–%.3f)",
      Odds_Ratio,
      conf.low,
      conf.high
    ),
    `p-value` = format_p(p.value)
  )

c2_note <- paste0(
  "Notes: Entries are interaction ratios of odds ratios from the pooled ",
  "quasibinomial model, with the dog-owner route as the reference. ",
  "Values below 1 indicate that the corresponding association was smaller ",
  "on the non-owner route. The joint test of all three interactions was ",
  "F(",
  joint_result$Df,
  ", ",
  joint_result$`Resid. Df`,
  ") = ",
  sprintf("%.3f", joint_result$F),
  ", p = ",
  format_p(joint_result$`Pr(>F)`),
  ". Confidence intervals are t-based."
)

table_c2_ft <- flextable(table_c2) %>%
  set_caption(
    caption = "Table C2. Pooled route-interaction tests"
  ) %>%
  theme_booktabs() %>%
  font(
    fontname = "Times New Roman",
    part = "all"
  ) %>%
  fontsize(
    size = 8.5,
    part = "all"
  ) %>%
  bold(part = "header") %>%
  align(
    j = c(
      "Ratio of ORs (95% CI)",
      "p-value"
    ),
    align = "center",
    part = "all"
  ) %>%
  valign(
    valign = "center",
    part = "all"
  ) %>%
  width(
    j = "Interaction",
    width = 3.5
  ) %>%
  width(
    j = "Ratio of ORs (95% CI)",
    width = 2.3
  ) %>%
  width(
    j = "p-value",
    width = 1
  ) %>%
  set_table_properties(
    layout = "fixed",
    width = 1,
    opts_word = list(
      split = FALSE,
      repeat_headers = TRUE
    )
  ) %>%
  add_footer_lines(
    values = c2_note
  ) %>%
  italic(part = "footer") %>%
  fontsize(
    size = 7.5,
    part = "footer"
  )

save_as_docx(
  table_c2_ft,
  path = "Appendix_Table_C2_Route_Interactions.docx",
  pr_section = prop_section(
    page_size = page_size(
      orient = "portrait"
    ),
    page_margins = page_mar(
      top = 0.6,
      bottom = 0.6,
      left = 0.6,
      right = 0.6
    )
  )
)
```


# Step 8
## Check
```{r}
stopifnot(
  person_period_data %>%
    group_by(ResponseId) %>%
    summarise(
      number_of_events = sum(event, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    summarise(
      maximum_events = max(number_of_events)
    ) %>%
    pull(maximum_events) <= 1
)
```


## Step 4.5: Node-level residual diagnostics for pooled Model 4
```{r}
# 1. Confirm the selected pooled model and required objects
stopifnot(
  exists("mod4"),
  exists("model_compare_agg"),
  exists("model_common_raw"),
  exists("pre_route_nodes")
)

cat(
  "Model used for Section 4.5: mod4\n",
  "Formula:",
  paste(deparse(formula(mod4)), collapse = " "),
  "\n"
)

# 2. Reconstruct the same model data while retaining node_id
diagnostic_grouping_vars <- c(
  "node_id",
  "time_5_c",
  "time_5_c_sq",
  "route_simplified",
  "has_text_entry",
  "financial_sensitivity",
  "privacy_level",
  "is_long_choice",
  "prompt_wc_10",
  "prompt_wc_band_tertile"
)

model_compare_node_agg <- model_common_raw %>%
  group_by(
    across(all_of(diagnostic_grouping_vars))
  ) %>%
  summarise(
    events = sum(events, na.rm = TRUE),
    trials = sum(trials, na.rm = TRUE),
    non_events = trials - events,
    .groups = "drop"
  ) %>%
  filter(trials > 0) %>%
  mutate(
    across(where(is.factor), fct_drop)
  )

stopifnot(
  sum(model_compare_node_agg$trials) ==
    sum(model_compare_agg$trials),

  sum(model_compare_node_agg$events) ==
    sum(model_compare_agg$events)
)
# 3. Obtain predictions from the existing mod4 model
# Use a new name so the dispersion_ratio() function is not overwritten
phi_mod4 <- sum(
  residuals(mod4, type = "pearson")^2
) / df.residual(mod4)

cat(
  "Model 4 dispersion ratio:",
  round(phi_mod4, 3),
  "\n"
)

cell_diagnostics <- model_compare_node_agg %>%
  mutate(
    predicted_hazard = predict(
      mod4,
      newdata = model_compare_node_agg,
      type = "response"
    ),

    predicted_hazard = pmin(
      pmax(predicted_hazard, 1e-8),
      1 - 1e-8
    ),

    expected_events =
      trials * predicted_hazard,

    binomial_variance =
      trials *
      predicted_hazard *
      (1 - predicted_hazard),

    # pre_route_nodes was defined before the route-specific models
    analysis_panel = case_when(
      node_id %in% pre_route_nodes ~
        "Pre-route / common nodes",

      as.character(route_simplified) %in%
        c("owner_main", "repeated_dogs_loop") ~
        "Dog-owner route",

      as.character(route_simplified) ==
        "non_owner_exit" ~
        "Non-owner route",

      TRUE ~
        "Unclassified"
    ),

    analysis_panel = factor(
      analysis_panel,
      levels = c(
        "Pre-route / common nodes",
        "Dog-owner route",
        "Non-owner route",
        "Unclassified"
      )
    )
  )

# No observations should remain unclassified
stopifnot(
  sum(
    cell_diagnostics$analysis_panel ==
      "Unclassified",
    na.rm = TRUE
  ) == 0
)
```


```{r}
# 5. Aggregate predictions and residuals to node level
node_residual_data <- cell_diagnostics %>%
  group_by(
    analysis_panel,
    node_id
  ) %>%
  summarise(
    trials =
      sum(trials, na.rm = TRUE),

    events =
      sum(events, na.rm = TRUE),

    expected_events =
      sum(expected_events, na.rm = TRUE),

    total_binomial_variance =
      sum(binomial_variance, na.rm = TRUE),

    .groups = "drop"
  ) %>%
  mutate(
    observed_hazard =
      events / trials,

    predicted_hazard =
      expected_events / trials,

    hazard_difference =
      observed_hazard -
      predicted_hazard,

    excess_breakoffs =
      events -
      expected_events,

    observed_expected_ratio =
      if_else(
        expected_events > 0,
        events / expected_events,
        NA_real_
      ),

    standardized_residual =
      excess_breakoffs /
      sqrt(
        phi_mod4 *
          total_binomial_variance
      )
  ) %>%
  group_by(analysis_panel) %>%
  mutate(
    panel_breakoff_share_pct =
      100 * events / sum(events)
  ) %>%
  ungroup() %>%
  arrange(
    analysis_panel,
    desc(standardized_residual)
  )

node_residual_data
```


## Appendix D1: Full_Node_Residual_Diagnostics
```{r}
d1_results <- node_residual_data %>%
  filter(
    excess_breakoffs > 0,
    is.finite(standardized_residual)
  ) %>%
  group_by(analysis_panel) %>%
  slice_max(
    order_by = standardized_residual,
    n = 5,
    with_ties = FALSE
  ) %>%
  arrange(
    desc(standardized_residual),
    .by_group = TRUE
  ) %>%
  mutate(
    Rank = row_number()
  ) %>%
  ungroup() %>%
  transmute(
    Panel = as.character(analysis_panel),
    Rank,
    Node = node_id,
    `At risk` = trials,
    Breakoffs = events,
    `Observed hazard` = observed_hazard,
    `Predicted hazard` = predicted_hazard,
    `O/E ratio` = observed_expected_ratio,
    `Standardized residual` = standardized_residual
  )

print(
  d1_results,
  n = Inf,
  width = Inf
)

write_csv(
  node_residual_data %>%
    arrange(
      analysis_panel,
      desc(standardized_residual)
    ),
  "Full_Node_Residual_Diagnostics.csv"
)
```

## Appendix_Table_D1_Residual_Diagnostics
```{r}
table_d1 <- d1_results %>%
  mutate(
    Panel = factor(
      Panel,
      levels = c(
        "Pre-route / common nodes",
        "Dog-owner route",
        "Non-owner route"
      ),
      labels = c(
        "Pre-route / common",
        "Dog-owner",
        "Non-owner"
      )
    )
  ) %>%
  arrange(Panel, Rank) %>%
  transmute(
    Panel = as.character(Panel),
    Rank = as.character(Rank),

    Node = gsub(
      "_",
      "_\n",
      Node,
      fixed = TRUE
    ),

    `At risk` = scales::comma(
      `At risk`,
      accuracy = 1
    ),

    Breakoffs = scales::comma(
      Breakoffs,
      accuracy = 1
    ),

    `Observed / predicted hazard` = sprintf(
      "%.2f%% / %.2f%%",
      100 * `Observed hazard`,
      100 * `Predicted hazard`
    ),

    `O/E ratio` = sprintf(
      "%.2f",
      `O/E ratio`
    ),

    `Standardized residual` = sprintf(
      "%.2f",
      `Standardized residual`
    )
  )

table_d1_ft <- flextable(table_d1) %>%
  set_caption(
    "Table D1. Largest positive standardized residuals by analytical panel"
  ) %>%
  set_header_labels(
    `At risk` = "At\nrisk",
    `Observed / predicted hazard` =
      "Observed /\npredicted hazard",
    `O/E ratio` = "O/E\nratio",
    `Standardized residual` =
      "Standardized\nresidual"
  ) %>%
  theme_booktabs() %>%
  font(
    fontname = "Times New Roman",
    part = "all"
  ) %>%
  fontsize(
    size = 7.5,
    part = "all"
  ) %>%
  bold(part = "header") %>%
  align(
    j = c(
      "Rank",
      "At risk",
      "Breakoffs",
      "Observed / predicted hazard",
      "O/E ratio",
      "Standardized residual"
    ),
    align = "center",
    part = "all"
  ) %>%
  align(
    j = c("Panel", "Node"),
    align = "left",
    part = "body"
  ) %>%
  valign(
    valign = "top",
    part = "all"
  ) %>%
  padding(
    padding = 2,
    part = "all"
  ) %>%
  width(j = "Panel", width = 0.85) %>%
  width(j = "Rank", width = 0.35) %>%
  width(j = "Node", width = 1.30) %>%
  width(j = "At risk", width = 0.65) %>%
  width(j = "Breakoffs", width = 0.65) %>%
  width(
    j = "Observed / predicted hazard",
    width = 1.20
  ) %>%
  width(j = "O/E ratio", width = 0.50) %>%
  width(
    j = "Standardized residual",
    width = 0.70
  ) %>%
  set_table_properties(
    layout = "fixed",
    width = 1,
    opts_word = list(
      split = FALSE,
      repeat_headers = TRUE
    )
  ) %>%
  add_footer_lines(
    paste(
      "Notes: Nodes were ranked separately within each analytical panel",
      "by their positive dispersion-adjusted standardized residuals.",
      "Up to five nodes are reported per panel; fewer are displayed when",
      "fewer than five positive residuals were available. Observed and",
      "predicted hazards are reported in that order. O/E denotes the",
      "observed-to-expected event ratio. Residuals are descriptive model",
      "diagnostics and should not be interpreted as causal effects."
    )
  ) %>%
  italic(part = "footer") %>%
  fontsize(
    size = 7,
    part = "footer"
  )

save_as_docx(
  table_d1_ft,
  path = "Appendix_Table_D1_Residual_Diagnostics.docx",
  pr_section = prop_section(
    page_size = page_size(
      orient = "portrait"
    ),
    page_margins = page_mar(
      top = 0.6,
      bottom = 0.6,
      left = 0.6,
      right = 0.6
    )
  )
)
```




## Figure_6_Observed_vs_Predicted_Hazards_by_Route
```{r}
# Label up to five largest positive residuals in each panel
label_nodes <- node_residual_data %>%
  filter(
    excess_breakoffs > 0,
    is.finite(standardized_residual)
  ) %>%
  group_by(analysis_panel) %>%
  slice_max(
    order_by = standardized_residual,
    n = 5,
    with_ties = FALSE
  ) %>%
  ungroup()

# Use the same x- and y-axis limits across all panels
axis_max <- max(
  c(
    node_residual_data$observed_hazard,
    node_residual_data$predicted_hazard
  ),
  na.rm = TRUE
) * 1.05

figure_observed_predicted <- ggplot(
  node_residual_data,
  aes(
    x = predicted_hazard,
    y = observed_hazard,
    size = trials
  )
) +
  # Perfect prediction line
  geom_abline(
    intercept = 0,
    slope = 1,
    linetype = "dashed",
    colour = "grey45",
    linewidth = 0.7
  ) +

  # All questionnaire nodes
  geom_point(
    colour = "#2C6E9B",
    alpha = 0.60
  ) +

  # Highlight residual hotspots
  geom_point(
    data = label_nodes,
    colour = "#B03A2E",
    alpha = 0.90
  ) +

  # Node labels
  geom_text_repel(
    data = label_nodes,
    aes(label = node_id),
    size = 3.4,
    colour = "#7B241C",
    box.padding = 0.45,
    point.padding = 0.30,
    min.segment.length = 0,
    max.overlaps = Inf,
    seed = 123,
    show.legend = FALSE
  ) +

  facet_wrap(
    ~ analysis_panel,
    ncol = 1,
    drop = TRUE
  ) +

  scale_x_continuous(
    labels = label_percent(accuracy = 0.1),
    expand = expansion(mult = c(0.01, 0.03))
  ) +

  scale_y_continuous(
    labels = label_percent(accuracy = 0.1),
    expand = expansion(mult = c(0.01, 0.03))
  ) +

  scale_size_area(
    max_size = 10,
    labels = label_comma()
  ) +

  coord_cartesian(
  xlim = c(0, axis_max),
  ylim = c(0, axis_max),
  clip = "off"
  ) +

  labs(
    title = paste(
      "Observed and pooled-model-predicted",
      "node-level breakoff hazards"
    ),
    subtitle = paste(
      "Predictions are from the final pooled",
      "quasibinomial discrete-time hazard model"
    ),
    x = "Model-predicted conditional breakoff hazard",
    y = "Observed conditional breakoff hazard",
    size = "Respondent-node exposures",
    caption = paste0(
  "The dashed equality line represents exact agreement.\n",
  "Labels identify up to five nodes with the largest positive ",
  "dispersion-scaled residuals in each panel."
)
  ) +

  theme_classic(base_size = 12) +

  theme(
    strip.background = element_rect(
      fill = "#EDF2F7",
      colour = NA
    ),
    strip.text = element_text(
      face = "bold"
    ),
    legend.position = "bottom",
    plot.title = element_text(
      face = "bold"
    ),
    plot.subtitle = element_text(
      colour = "grey30"
    ),
    plot.caption = element_text(
      colour = "grey35",
      hjust = 0
    ),
    plot.margin = margin(
      t = 10,
      r = 30,
      b = 10,
      l = 10
    )
  )

figure_observed_predicted

ggsave(
  filename =
    "figure6-observed-predicted-hazards-by-route.png",
  plot = figure_observed_predicted,
  width = 7.2,
  height = 10.8,
  units = "in",
  dpi = 600,
  bg = "white"
)
```


```{r}
panel_model_fit_summary <- cell_diagnostics %>%
  group_by(analysis_panel) %>%
  summarise(
    number_of_nodes =
      n_distinct(node_id),

    exposures =
      sum(trials, na.rm = TRUE),

    observed_events =
      sum(events, na.rm = TRUE),

    predicted_events =
      sum(expected_events, na.rm = TRUE),

    excess_breakoffs =
      observed_events - predicted_events,

    observed_hazard =
      observed_events / exposures,

    predicted_hazard =
      predicted_events / exposures,

    observed_expected_ratio =
      observed_events / predicted_events,

    .groups = "drop"
  )

print(
  panel_model_fit_summary,
  n = Inf,
  width = Inf
)
```


```{r}
overall_model_fit_summary <- cell_diagnostics %>%
  summarise(
    exposures =
      sum(trials, na.rm = TRUE),

    observed_events =
      sum(events, na.rm = TRUE),

    predicted_events =
      sum(expected_events, na.rm = TRUE),

    prediction_difference =
      observed_events - predicted_events,

    observed_hazard =
      observed_events / exposures,

    predicted_hazard =
      predicted_events / exposures
  )

overall_model_fit_summary
```

## table 6
```{r}
selected_hotspot_lookup <- tribble(
  ~node_id, ~question_topic, ~response_format, ~display_order,

  "Q1_DogNumber",
  "Number of dogs owned",
  "Single choice",
  1,

  "Q13.2_HolidayAccommo",
  "Holiday accommodation arrangements",
  "Multiple choice with optional text",
  2,

  "Q17.1_ServicesCutCoL",
  "Services reduced due to cost of living",
  "Multiple choice",
  3,

  "Q22_ImproveLife",
  "Ways to improve dogs' lives",
  "Open text",
  4,

  "Q26_Ethnicity",
  "Respondent ethnicity",
  "Choice list with optional text",
  5,

  "E2FutureDogOwner",
  "Future dog ownership",
  "Single choice",
  6,

  "E3_FutureDogSource",
  "Expected source of a future dog",
  "Multiple choice",
  7,

  "E3.1_NotRescue",
  "Reasons for not using a rescue",
  "Multiple choice",
  8
)

selected_hotspot_profiles <-
  node_residual_data %>%
  inner_join(
    selected_hotspot_lookup,
    by = "node_id"
  ) %>%
  arrange(display_order)

stopifnot(
  nrow(selected_hotspot_profiles) == 8,
  !anyNA(selected_hotspot_profiles$question_topic),
  !anyNA(selected_hotspot_profiles$response_format)
)

selected_hotspot_profiles_display <-
  selected_hotspot_profiles %>%
  transmute(
    Panel = as.character(analysis_panel),

    Node = node_id,

    `Question topic` = question_topic,

    `Response format` = response_format,

    `Observed hazard` = scales::percent(
      observed_hazard,
      accuracy = 0.01
    ),

    `Predicted hazard` = scales::percent(
      predicted_hazard,
      accuracy = 0.01
    ),

    `O/E ratio` = sprintf(
      "%.2f",
      observed_expected_ratio
    ),

    `Excess breakoffs` = scales::comma(
      round(excess_breakoffs),
      accuracy = 1
    )
  )

print(
  selected_hotspot_profiles_display,
  n = Inf,
  width = Inf
)
```


```{r}
hotspot_profile_table <- selected_hotspot_profiles_display %>%
  flextable() %>%
  theme_booktabs() %>%
  bold(
    part = "header"
  ) %>%
  align(
    j = c(
      "Observed hazard",
      "Predicted hazard",
      "O/E ratio",
      "Excess breakoffs"
    ),
    align = "center",
    part = "all"
  ) %>%
  valign(
    valign = "top",
    part = "all"
  ) %>%
  autofit() %>%
  fontsize(
    size = 9,
    part = "all"
  ) %>%
  set_caption(
    caption =
      "Table 6. Selected residual hotspot profiles"
  ) %>%
  add_footer_lines(
    values = paste(
      "Notes: O/E denotes the observed-to-expected event ratio.",
      "Excess breakoffs are descriptive model residuals and should",
      "not be interpreted as the number of breakoffs that would",
      "necessarily be prevented by redesigning the question."
    )
  )

hotspot_profile_table
```


```{r}
# Portrait version: Selected residual hotspot profiles
# 1. Prepare a narrower display table
hotspot_profile_portrait <- selected_hotspot_profiles_display %>%
  transmute(
    Route = gsub(
  " route$| / common nodes$",
  "",
  as.character(Panel)
),

    # Allow long node names to wrap
    Node = gsub(
      "_",
      "_\n",
      Node,
      fixed = TRUE
    ),

    `Question topic` = `Question topic`,

    `Response format` = `Response format`,

    `Observed / predicted hazard` = paste0(
      `Observed hazard`,
      " / ",
      `Predicted hazard`
    ),

    `O/E ratio` = `O/E ratio`,

    `Excess breakoffs` = `Excess breakoffs`
  )


# 2. Create the portrait table
hotspot_profile_table <- hotspot_profile_portrait %>%
  flextable() %>%

  set_header_labels(
    Route = "Route",
    Node = "Node",
    `Question topic` = "Question topic",
    `Response format` = "Response\nformat",
    `Observed / predicted hazard` =
      "Observed /\npredicted hazard",
    `O/E ratio` = "O/E\nratio",
    `Excess breakoffs` = "Excess\nbreakoffs"
  ) %>%

  theme_booktabs() %>%

  # Fixed layout prevents long text from expanding the table
  set_table_properties(
    layout = "fixed",
    width = 1,
    align = "center"
  ) %>%

  # Column widths suitable for a portrait page
  width(
    j = "Route",
    width = 0.65
  ) %>%

  width(
    j = "Node",
    width = 0.90
  ) %>%

  width(
    j = "Question topic",
    width = 1.55
  ) %>%

  width(
    j = "Response format",
    width = 0.85
  ) %>%

  width(
    j = "Observed / predicted hazard",
    width = 0.95
  ) %>%

  width(
    j = "O/E ratio",
    width = 0.45
  ) %>%

  width(
    j = "Excess breakoffs",
    width = 0.65
  ) %>%

  # Formatting
  font(
    fontname = "Times New Roman",
    part = "all"
  ) %>%

  fontsize(
    size = 8,
    part = "all"
  ) %>%

  bold(
    part = "header"
  ) %>%

  align(
    j = c(
      "Observed / predicted hazard",
      "O/E ratio",
      "Excess breakoffs"
    ),
    align = "center",
    part = "all"
  ) %>%

  align(
    j = c(
      "Route",
      "Node",
      "Question topic",
      "Response format"
    ),
    align = "left",
    part = "body"
  ) %>%

  valign(
    valign = "top",
    part = "all"
  ) %>%

  padding(
    padding.top = 3,
    padding.bottom = 3,
    padding.left = 2,
    padding.right = 2,
    part = "all"
  ) %>%

  set_caption(
    caption =
      "Table 6. Selected residual hotspot profiles"
  ) %>%

  add_footer_lines(
    values = paste(
      "Notes: Observed and predicted hazards are reported in that order.",
      "O/E denotes the observed-to-expected event ratio.",
      "Excess breakoffs are descriptive model residuals and should not",
      "be interpreted as the number of breakoffs that would necessarily",
      "be prevented by redesigning the question."
    )
  ) %>%

  italic(
    part = "footer"
  ) %>%

  fontsize(
    size = 7,
    part = "footer"
  )


# 3. Display the table in R
hotspot_profile_table
```



```{r}
output_file <-
  "Table_Selected_Residual_Hotspot_Profiles_Portrait.docx"

save_as_docx(
  hotspot_profile_table,
  path = output_file
)
```



## output svg figure
```{r}
# Create output folder if it does not already exist
dir.create(
  "media/figures",
  recursive = TRUE,
  showWarnings = FALSE
)

save_svg <- function(plot_object,
                     filename,
                     width,
                     height) {

  ggsave(
    filename = file.path(
      "media/figures",
      filename
    ),
    plot = plot_object,
    device = svglite::svglite,
    width = width,
    height = height,
    units = "in",
    bg = "white"
  )
}


# Figure 3: overall and route-conditional survival
save_svg(
  plot_object = figure3_overall_route_survival,
  filename =
    "figure3-overall-route-survival.svg",
  width = 10,
  height = 10
)


# Figure 4: raw attrition hotspots
save_svg(
  plot_object = figure4_raw_attrition_hotspots,
  filename =
    "figure4-raw-attrition-hotspots.svg",
  width = 7.2,
  height = 8.4
)


# Figure 5: adjusted odds ratios from Model 4
save_svg(
  plot_object = figure5_model4_adjusted_odds_ratios,
  filename =
    "figure5-model4-adjusted-odds-ratios.svg",
  width = 7.2,
  height = 4.8
)


# Figure 6: observed versus predicted hazards
save_svg(
  plot_object = figure_observed_predicted,
  filename =
    "figure6-observed-predicted-hazards-by-route.svg",
  width = 7.2,
  height = 10.8
)
```








